### 2015-01-20 paper/Diversity_MS.tex
First commit for diversity paper repository

% Preamble
\documentclass[12pt,a4paper]{article}
\usepackage{enumerate} 	% put in numbers or bullet points
\usepackage{setspace}	% line spacing					
\usepackage{authblk}	% For author affiliations
\usepackage{graphicx} 	% For adding pictures

\usepackage[nomarkers]{endfloat} %Figures and tables at the end of the document
\usepackage{pdflscape}	% for landscape pages
\usepackage{mathtools}	% For equations etc.
\usepackage[osf]{mathpazo} % palatino font package
\usepackage{fixltx2e}	% includes subscripts
\usepackage{ms}     	% load the manuscript style template - may need to change this for PeerJ

\setcounter{secnumdepth}{0} % removes numbers from section headings
\raggedright 			% justify the text on the left only
\pagenumbering{arabic}	% Page numbers

\usepackage[round]{natbib} % author-year citations in round brackets

%-----------------------------------------
%Title page? NB PeerJ say that they don't need a title page
%----------------------------------------
\title{}

\author{Sive Finlay$^{1,2}$ and Natalie Cooper$^{1,2,*}$}
\affiliation{\noindent{\footnotesize
$^1$ School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\ 
$^2$ Trinity Centre for Biodiversity Research, Trinity College Dublin, Dublin 2, Ireland.\\
$^*$Corresponding author: ncooper@tcd.ie; Zoology Building, Trinity College Dublin, Dublin 2, Ireland.\\ Tel: +353 1 896 1926.\\}}
\date{}	% To give blank date

\runninghead{Cranial morphological diversity in tenrecs }

\keywords{geometric morphometrics, golden moles, morphological diversity, tenrecs}
%---------------------------------------------------------------
% Start of document
\begin{document}
\modulolinenumbers[1] 	% Line numbering on every line

\mstitlepage			% Instead of \maketitle you can use the nice template to get it looking like a manuscript
\parindent=1.5em		% Changes paragraph indenting so it's not so big
\addtolength{\parskip}{.3em} % Changes spacing between sections so it's smaller
%****************************************************

%Abstract in a separate document for PeerJ
%****************************************************
\section{Introduction}

%************************************
\section{Materials and Methods}

%*********************************
\section{Results and Discussion}

%**********************************
\section{Conclusions}

%*******************************
\section{Acknowledgements}

%********************************
\bibliographystyle{sysbio} 
\bibliography{refs_disparity} %This is a copy of my refs_thesis file so it has more references than are included in the paper

\end{document}

### 2015-01-21 paper/Diversity_MS.tex
practice change
Intro and first part of methods from thesis

@@
 
+	Analysing patterns of morphological diversity has important implications for our understanding of ecological and evolutionary traits.
+For example, from a functional ecology perspective, morphological characteristics of limbs inform us about locomotory style \citep[e.g.][]{Bou1987} and the trophic niches associated with particular dental morphologies affect speciation and diversification rates through time \citep{Price2012}.
+Morphological diversity is also an important aspect of evolutionary patterns such as adaptive radiations and convergent evolution.
+High morphological diversity is a unifying \citep{Losos2010a, Olson2009}, although not defining \citep{Glor2010, Olson2009}, characteristic of adaptive radiations.
+Furthermore, analysing morphological convergences in groups such as freshwater cichlid fish \citep{Muschick2012} and anole lizards \citep{Mahler2013} gives interesting insights into the relative repeatability of evolution \citep{Losos2011}.
+
+	Although studies of morphological diversity have clear implications for our understanding of ecological and evolutionary patterns, apart from a few examples \citep[e.g.][]{Ruta2013, Goswami2011, Brusatte2008}, it is still common to study morphological diversity from a qualitative rather than quantitative perspective.
+However, we need to quantify the morphological similarities and differences among species to gain a better understanding of their ecological interactions and evolutionary history.
+Unfortunately, morphological diversity is difficult to quantify.
+Studies are inevitably constrained to measure the diversity of specific traits rather than overall morphologies \citep{Roy1997}.
+In addition, our perception of morphological diversity is influenced by the trait being used.
+One study of pterosaurs demonstrated that comparing the diversity of different morphological traits using varying methods produced similar results \citep{Foth2012}.
+However, it remains unclear whether this finding can be applied to all vertebrate groups: in some species, comparing the relative diversity of cranial and limb morphologies may yield different results \citep{Foth2012}.
+Furthermore, linear measurements of morphological traits can restrict our understanding of overall morphological variation.
+A distance matrix of measurements between specific points is unlikely to give a completely accurate representation of a three dimensional structure \citep{Rohlf1993}.
+
+	These are important limitations to consider but geometric morphometric approaches help to overcome some of the issues associated with traditional morphological studies \citep{Adams2004}.
+Morphometric studies based on caliper measurements of particular features can only describe a limited set of distances, ratios and angles which often fail to capture the overall shape of a specific structure \citep{Slice2007}.
+Geometric morphometrics circumvents these issues by using a system of Cartesian landmark coordinates to define anatomical points.
+This method captures more of the true, overall anatomical shape of particular structures \citep{Mitteroecker2009}.
+These more detailed approaches are useful tools for studying patterns of morphological diversity.
+
+	Here we apply geometric morphometric techniques to quantify morphological diversity in a Family of small mammals, the tenrecs.
+Tenrecs (Afrosoricida, Tenrecidae) are a morphologically diverse group that is commonly cited as an example of both convergent evolution and an adaptive radiation \citep{Soarimalala2011, Eisenberg1969}.
+The Family is comprised of 34 species, 31 of which are endemic to Madagascar \citep{Olson2013}.
+Body masses of tenrecs span three orders of magnitude (2.5 to > 2,000g); a greater range than all other Families, and most Orders, of living mammals \citep{Olson2003}.
+Within this vast size range there are tenrecs which convergently resemble shrews (\textit{Microgale} tenrecs), moles (\textit{Oryzorictes} tenrecs) and hedgehogs \citep[\textit{Echinops} and \textit{Setifer} tenrecs,][]{Eisenberg1969}.
+Their similarities include examples of morphological, behavioural and ecological convergence \citep{Soarimalala2011}.
+Tenrecs are one of only four endemic mammalian clades in Madagascar and the small mammal species they resemble are absent from the island \citep{Garbutt1999}.
+Therefore, it appears that tenrecs represent an adaptive radiation of species which filled otherwise vacant ecological niches \citep{Soarimalala2011}.
+	The similarities among tenrecs and other small mammals are even more remarkable when you consider their phylogenetic history.
+Tenrecs were originally classified within the general "Insectivora" clade and only molecular studies revealed their true phylogenetic affinities within the Afrotherian mammals \citep{Stanhope1998}.
+Therefore, despite initial appearances, tenrecs are more closely related to elephants, manatees and aardvarks than they are to shrews, moles or hedgehogs.
+
+	Although tenrecs are often cited as an example of both an adaptive radiation and exceptional convergent evolution, these claims have not been investigated quantitatively.
+There are qualitative similarities among the hind limb morphologies of tenrecs and several other unrelated species with similar locomotory styles \citep{Salton2009} but the degree of morphological similarity has not been established.
+Morphological diversity is an important feature of adaptive radiations \citep{Losos2010a} and it also informs our understanding of convergent phenotypes \citep{Muschick2012}.
+Therefore, it is important to quantify patterns of morphological diversity in tenrecs to gain an insight into their evolution.
+My thesis is the first study to address this issue.
+
+	We present the first quantitative study of patterns of morphological diversity in tenrecs.
+We use geometric morphometric techniques \citep{Rohlf1993} to compare cranial morphological diversity in tenrecs to that of their closest relatives, the golden moles (Afrosoricida, Chrysochloridae).
+	We expect tenrecs to be more morphologically diverse than golden moles because tenrecs occupy a wider variety of ecological niches.
+The tenrec Family includes terrestrial, semi-fossorial, semi-aquatic and semi-arboreal species \citep{Soarimalala2011}.
+In contrast, all golden moles occupy very similar, fossorial ecological niches \citep{Bronner1995}.
+Greater ecological variety is often (though not always) correlated with higher morphological diversity \citep{Losos2010a}.
+
+	%Finish off this introduction
 %************************************
@@
 
+%Overview section: data, geometric morphometrics, measuring diversity
+
+	The methods we used involved several steps of data collection, geometric morphometrics analyses and comparisons of morphological diversity.
+For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.
+
+%Methods flow chart
+	\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=1\linewidth,height=0.8\textheight]{figures/methods_flowchart_paper.png}
+
+	\caption[Flowchart diagram of data collection and analysis]
+		{Summary of the main steps in our data collection, processing and analysis protocol.
+Note that the analyses were repeated separately for each set of photographs: skulls in dorsal, ventral and lateral views.
+The dashed arrows refer to the stage at which we selected a subsample of the tenrecs (including just five species of the \textit{Microgale} Genus) so that we could compare the morphological diversity of this reduced subsample of tenrec species to the diversity of golden moles.}
+
+		\label{fig:flow}
+		\end{figure}
+
+\subsection{Data collection}
+	One of us (SF) used the collections of five museums: the Natural History Museum, London (BMNH), the Smithsonian Institute Natural History Museum, Washington D.C.
+(SI), the American Museum of Natural History, New York (AMNH), the Museum of Comparative Zoology, Cambridge M.A.
+(MCZ) and the Field Museum of Natural History, Chicago (FMNH).
+We recorded species names as they were written on museum specimen labels and then corrected them to match the taxonomy in Wilson and Reeder's Mammal Species of the World \citeyearpar{Wilson2005}.
+For recently identified species,  which are not included in Wilson and Reeder \citeyearpar{Wilson2005}, we used the taxonomy recorded on the specimen labels.
+Wilson and Reeder \citeyearpar{Wilson2005} record 30 species of tenrec but more recent studies indicate that there are now 34 species \citep[][]{Olson2013}.
+The additional species belong to the shrew tenrec (\textit{Microgale}) Genus and represent either recognition of cryptic species boundaries \citep{Olson2004} or discovery of new species \citep{Goodman2006, Olson2009}.
+Only one of these four recent additions, \textit{M.
+jobihely}, was present in the museum collections and therefore we could not include the three other newly recognised species in the analyses.
+ 	We photographed all of the tenrec and golden mole skulls available in the collections.
+This included 31 of the 34 species in the tenrec Family and 12 of the 21 species of golden moles \citep{Wilson2005}.
+	%Left out the points about male/female and adult/juvenile
+
+	We took pictures of the skulls using photographic copy stands consisting of a camera attachment with an adjustable height bar, a flat stage on which to place the specimen and an adjustable light source.
+To take possible light variability into account, on each day we took a photograph of a white sheet of paper and used the custom white balance function on the camera to set the image as the baseline "white" measurement for those particular light conditions.
+
+	We photographed the specimens with a Canon EOS 650D camera fitted with a EF 100 mm f/2.8 Macro USM lens.
+We used a remote control (H\"ahnel Combi TF) to take the photos to avoid shaking the camera and distorting the images.
+We photographed the specimens on a black material background with a light source in the top left-hand corner of the photograph.
+We used small bean bags as necessary to hold the specimens in position while being photographed to ensure that they lay in a flat plane relative to the camera and did not tilt in any direction.
+We used the grid-line function on the live-view display screen of the camera to position the specimens in the centre of each image.
+
+	We photographed the skulls in three views: dorsal (top of the cranium), ventral (underside of the skull with the palate roof facing upwards) and lateral (right side of the skull).
+When the right sides of the skulls were damaged or incomplete we photographed the left sides and later reflected the images so that they could be compared to pictures of the right sides \citep[e.g.][]{Barrow2008}.
+
+	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files %\citep[uncompressed files preserve greater detail,][]{RHOI2013}.
+Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull pictures along with the mandibles \citep{Finlay2013m}.
+Copyright restrictions from the other museums prevent public sharing of their images however they are available on request.
+
+%-----------------------------------------
+\subsection{Geometric morphometric analyses}
+
+\subsubsection{Landmark placement on images}
+
+	We used a combination of landmark and semilandmark analysis approaches to assess the shape variability in skull.
+We used the TPS software suite \citep{Rohlf2013} to digitise landmarks and curves on the photos.
+We set the scale on each image individually to standardise for the different camera heights that I used when photographing my specimens.
+We created separate data files for each of the three morphometric analyses (skulls in dorsal, ventral and lateral views).
+One of us (SF) digitised landmarks and semilandmark points on every image individually.
+Some specimens were too damaged to use in particular views so there were a different total number of images for each analysis: skulls dorsal (356), ventral (346) and lateral (336).
+	%Numbers are from the two_family_disparity script after cleaning up the data to remove damages specimens
+
+	When using semilandmark approaches there is a potential problem of over - sampling: simpler structures will require fewer semilandmarks to accurately represent their shape  \citep{MacLeod2012}.
+To ensure that we applied a uniform standard of shape representation to each outline segment (i.e.
+that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012}.
+For each data set we chose a random selection of photos of specimens which represented the breadth of the morphological data (i.e.
+specimens from each sub-group of species).
+We drew the appropriate curves on each specimen and over-sampled the number of points on the curves.
+We measured the length of the line and regarded that as the 100\%, true length of that outline.
+We then re-sampled the curves with decreasing numbers of points and measured the length of the outlines.
+We calculated the length of each re-sampled curve as a percentage of the total length of the curve and then found the average percentage length for that reduced number of semilandmark points across all of the specimens in my test file.
+We continued this process until I found the minimum number of points that gave a curve length which was at least 95\% accurate.
+We repeated these curve-sampling tests for each analysis to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.
+
+	Figure (REF) depicts that landmarks and curves which we used for each of the sets of photographs.
+For landmarks which are defined by dental structures, we used published dental sources \citep{Repenning1967, Eisenberg1969, Nowak1983, MacPhee1987, KnoxJones1992, Davis1997, Querouil2001, Nagorsen2002, Wilson2005, Goodman2006, Karatas2007, Hoffmann2008, Asher2008,  Muldoon2009, Lin2010} where available to identify the number and type of teeth in each species.
+Detailed descriptions of the landmarks can be found in the supplementary material.
+	%Put the landmark tables into supplementary
+
+	%Add the landmarks picture: three skulls together
+
+	%Maybe put morphometrics error checking into the supplementary as well?
 %*********************************
@@
 \bibliographystyle{sysbio} 
-\bibliography{refs_disparity} %This is a copy of my refs_thesis file so it has more references than are included in the paper
+\bibliography{refs_thesis} %This is a copy of my refs_thesis file so it has more references than are included in the paper
 

### 2015-01-21 paper/Diversity_MS.tex
Fixed reference bugs

@@
 \usepackage{ms}     	% load the manuscript style template - may need to change this for PeerJ
+\usepackage{hyperref}
 
@@
 For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.
-
 %Methods flow chart
@@
 
-	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files %\citep[uncompressed files preserve greater detail,][]{RHOI2013}.
+	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep{RHOI2013}. 
 	Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull pictures along with the mandibles \citep{Finlay2013m}.
@@
 \bibliographystyle{sysbio} 
-\bibliography{refs_thesis} %This is a copy of my refs_thesis file so it has more references than are included in the paper
+\bibliography{refs_paper}
 

### 2015-01-21 paper/Diversity_MS.tex
Added thesis results

@@
 \usepackage{ms}     	% load the manuscript style template - may need to change this for PeerJ
-\usepackage{hyperref}
+\usepackage{hyperref} %need this for url references
 
@@
 The dashed arrows refer to the stage at which we selected a subsample of the tenrecs (including just five species of the \textit{Microgale} Genus) so that we could compare the morphological diversity of this reduced subsample of tenrec species to the diversity of golden moles.}
-
 		\label{fig:flow}
@@
 
-	We photographed the skulls in three views: dorsal (top of the cranium), ventral (underside of the skull with the palate roof facing upwards) and lateral (right side of the skull).
+	We photographed the skulls in three views: dorsal (top of the cranium), ventral (underside of the skull with the palate roof facing upwards) and lateral (right side of the skull) (Figure \ref{fig:flow}).
 When the right sides of the skulls were damaged or incomplete we photographed the left sides and later reflected the images so that they could be compared to pictures of the right sides \citep[e.g.][]{Barrow2008}.
 
-	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep{RHOI2013}. 
+	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}. 
 	Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull pictures along with the mandibles \citep{Finlay2013m}.
@@
 One of us (SF) digitised landmarks and semilandmark points on every image individually.
-Some specimens were too damaged to use in particular views so there were a different total number of images for each analysis: skulls dorsal (356), ventral (346) and lateral (336).
-	%Numbers are from the two_family_disparity script after cleaning up the data to remove damages specimens
+Some specimens were too damaged to use in particular views so there were a different total number of images for each analysis.
+We photographed 182 skulls in dorsal view (148 tenrecs and 34 golden moles), 173 skulls in ventral view (141 tenrecs and 32 golden moles) and 171 skulls in lateral view (140 tenrecs and 31 golden moles).
 
@@
 Detailed descriptions of the landmarks can be found in the supplementary material.
+%****************************************************
 	%Put the landmark tables into supplementary
@@
 	%Maybe put morphometrics error checking into the supplementary as well?
+%***************************************************
+
+	After creating the files with the landmarks and semilandmarks placed on each photograph, we used TPSUtil \citep{Rohlf2012} to create "sliders" files that defined which points in the TPS files should be treated as semilandmarks \citep{Zelditch2012}.
+We combined the landmarks and taxonomic identification files into a single morphometrics data object and carried out all further analyses in R version 3.1.1 \citep{Team2014}.
+Data and code for all of our analyses is available on GitHub (REF to paper repository).
+
+	At this stage, we either used the full data set (31 species of tenrec and 12 species of golden mole) or a reduced data set with just 17 species of tenrec (Figure \ref{fig:flow}).
+We created this reduced data set because the majority of tenrec species (19 out of 31 in my data) belong to the \textit{Microgale} (shrew-like) Genus that has relatively low morphological diversity \citep{Soarimalala2011, Jenkins2003}.
+This may mask signals of higher morphological diversity among other tenrecs.
+To test this, we created a subset of the tenrec data that included just five of the \textit{Microgale} species, each representing one of the five sub-divisions of \textit{Microgale} outlined by Soarimalala and Goodman \citeyearpar{Soarimalala2011}, i.e.
+small, small-medium, medium, large and long-tailed species.
+We compared the morphological diversity of this subset of tenrecs (n=17: five \textit{Microgale} and 12 non-\textit{Microgale} species) to that of the 12 species of golden moles (dashed arrows in Figure \ref{fig:flow}).
+After this selection stage, all further steps in the analyses were the same.
+
+	For each analysis, we used the gpagen function in the geomorph package \citep{Adams2013} to run a general Procrustes alignment \citep{Rohlf1993} of the landmark coordinates while sliding the semilandmarks by minimising Procrustes distance \citep{Bookstein1997}.
+We used these Procrustes-aligned coordinates of all specimens to calculate average shape values for each species which we then used for a principal components (PC) analysis with the plotTangentSpace function \citep{Adams2013}.
+We selected the number of principal component (PC) axes that accounted for 95\% of the variation in the data (Figure \ref{fig:flow}) and used these axes to estimate morphological diversity in each Family.
+%-------------------------------------------------------	
+\subsection{Estimating morphological diversity}
+
+	We grouped the PC scores for tenrecs and golden moles separately so that we could estimate the diversity of each Family and then compare the two groups (Figure \ref{fig:flow}).
+We compared morphological diversity in two ways.
+First, we used non parametric multivariate analysis of variance \citep[npMANOVA;][]{Anderson2001} to test whether tenrecs and golden moles occupied significantly different positions within the morphospaces defined by the PC axes that accounted for 95\% of the overall variation in the data \citep[e.g.][]{Serb2011, Ruta2013}.
+A significant difference between the two Families would indicate that they have unique morphologies which do not overlap.
+Second, we compared morphological diversity within tenrecs to the diversity within golden moles.
+We define morphological diversity as the mean Euclidean distance (sum of squared differences) between each species and its Family centroid (Figure \ref{fig:centroids}).
+This is summarised in the equation below where \textit{n} is the number of species in the Family, \textit{i} is the number of PC axes and \textit{c} are the average PC scores for each axis (the centroid).
+
+	\begin{equation}
+	Disparity = \frac{\sqrt{\Sigma(PCn_{i}-PCc_{i})^2}}{n}
+	\end{equation}
+
+	If tenrecs are more morphologically diverse than golden moles, then they should be more dispersed within the morphospaces and have, on average, higher values of mean Euclidean distance.
+
+%Diagram of mean distance to centroid (based on the diagram in Cooper et al 2009)
+	\begin{figure}[!htbp]
+	\centering
+	\includegraphics [width=0.7\linewidth, height=0.7\textheight, keepaspectratio]{figures/Centroids.png}
+	\caption[Calculating diversity as mean Euclidean distance to Family centroid.]
+		{Estimating morphological diversity as the mean Euclidean distance between each species and the Family centroid.
+Every species had scores on the principal components (PC) axes that accounted for 95\% of the variation in the principal components analysis.
+The number of axes (PCn) varied for each analysis but they were the same within a single analysis.
+PC scores were used to calculate the Euclidean distance from each species to the Family centroid (average (\begin{math}
+			\bar{x}
+			\end{math}) PC scores for the entire Family). Morphological diversity of the Family is the average value of these Euclidean distances.}
+	\label{fig:centroids}
+	\end{figure}	
+%-------------------------------------------
+	One possible issue with these analyses is that the two Families have unequal sample sizes: 31 (or a subset of 17) tenrec species compared to just 12 golden mole species.
+Morphological diversity is usually decoupled from taxonomic diversity \citep[e.g.][]{Ruta2013, Hopkins2013} so larger groups are not necessarily more morphologically diverse.
+However, comparing morphological diversity in tenrecs to the diversity of a smaller Family could still bias the results.
+We used pairwise permutation tests to account for this potential issue.
+
+	We tested the null hypothesis that tenrecs and golden moles have the same morphological diversity (the same mean Euclidean distance to the Family centroid).
+If this is true, when we randomly assign the group identity of each species (i.e.
+shuffle the "tenrec" and "golden mole" labels) and then re-compare the morphological diversity of the two groups, there will be no significant difference between these results and those obtained when the species are assigned to the correct groupings.
+	We performed this shuffling procedure (random assignation of group identity) 1000 times and calculated the difference in morphological diversity between the two groups for each permutation.
+This generated a distribution of 1000 values which are calculations of the differences in morphological diversity under the assumption that the null hypothesis (equal morphological diversity in the two Families) is true.
+This method automatically accounts for differences in sample size because shuffling of the group labels preserves the sample size of each group: there will always be 12 species labelled as "golden mole" and then, depending on the analysis, either 31 or 17 species labelled as "tenrec".
+Therefore, the 1000 permuted values of differences in morphological diversity create a distribution of the expected difference in diversity between a group of sample size 31 (or 17 in the case of the subsetted tenrec data) compared to a group of sample size 12 under the null hypothesis that the two groups have the same morphological diversity.
+We compared the observed measures of the differences in morphological diversity between the two Families to these null distributions to determine whether there were significant differences after taking sample size into account (two-tailed t test).
 %*********************************
-\section{Results and Discussion}
+\section{Results and Discussion} %PeerJ asks for these two sections to go together
 
+\subsection{Results}
+	Figure (REF to PCA) depicts the morphospaces defined by the first two principal component (PC) axes from our principal components analyses (PCAs) of skull and mandible morphologies.
+The PCAs are based on the average Procrustes -superimposed shape coordinates for skulls in three views (dorsal, ventral and lateral).
+%-----------------------------
+%PCA figure with three plots
+
+%--------------------------
+	To compare morphological diversity in the two families, we used the PC axes which accounted for 95\% of the cumulative variation in each of the skull analyses: dorsal (n=6 axes), ventral (n=7 axes) and lateral (n=7 axes).
+First, we compared the position of each Family within the morphospace plots.
+Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001 ), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72 , p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001 ) skull morphospaces,  indicating that the Families have very different, non-overlapping cranial and mandible morphologies (REF PCA figure).
+
+	Second, we compared the morphological diversity within each Family.
+Based on our measures of mean Euclidean distance to the Family centroids, tenrec skulls are more morphologically diverse than golden mole skulls when they are measured in lateral view but not in dorsal or ventral view (Table \ref{tab:diversity}).
+In contrast, when we analysed morphological diversity of skulls within the sub-sample of 17 tenrecs (including just five \textit{Microgale} species) compared to the 12 golden mole species, we found that tenrec skulls were significantly more morphologically diverse than golden moles in all analyses (Table \ref{tab:diversity}).
+
+%----------------------------------------
+%Results table: I changed the format to make it fit better
+
+	\begin{table}[!htbp]			
+		\caption[Comparing morphological diversity in tenrecs and golden moles.]
+		{Morphological diversity in tenrecs compared to golden moles (12 species).
+N is the number of tenrec species: 31 species or 17 species including just five representatives of the \textit{Microgale} Genus.
+Morphological diversity of the Family is the mean Euclidean distance from each species to the Family centroid.
+Significant differences between the two Families (p$<$0.05) from two-tailed t-tests are highlighted in bold.}
+		\input{tables/diversity.results} 
+		\label{tab:diversity}  
+	\end{table}
+
+%---------------------------------------------
+	The pairwise permutation tests for each analysis confirmed that differences in morphological diversity were not artefacts of differences in sample size (Table \ref{tab:permutations})
+%--------------------------------------------	
+\begin{table}[!htbp]			
+	\caption[Results of the permutation tests]{Results of the permutation analyses comparing the observed differences in morphological diversity to a null distribution of expected results.
+Morphological diversity of the Family is the mean Euclidean distance from each species to the Family centroid.
+Results are shown for both the full (N=31 species of tenrec compared to 12 species of golden mole) and reduced (N=17 species of tenrec compared to 12 golden moles) data sets.
+Significant values (p$<$0.05) indicate that the observed morphological diversity is different to the expected differences under a null hypothesis of equivalent diversities in the two Families.}
+		\input{tables/perm.results} 
+		\label{tab:permutations}  
+	\end{table}
+%----------------------------------
+\subsection{Discussion}
 %**********************************

### 2015-01-27 paper/Diversity_MS.tex
Added discussion, acknowledgements and PCA figures

@@
 \subsection{Results}
-	Figure (REF to PCA) depicts the morphospaces defined by the first two principal component (PC) axes from our principal components analyses (PCAs) of skull and mandible morphologies.
+	Figure \ref{fig:threePCA} depicts the morphospaces defined by the first two principal component (PC) axes from our principal components analyses (PCAs) of skull and mandible morphologies.
 The PCAs are based on the average Procrustes -superimposed shape coordinates for skulls in three views (dorsal, ventral and lateral).
@@
 %PCA figure with three plots
-
+%PCA figure
+	%From the diversity_PCAplots_3panel
+	\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/PCA_threeplot.png}
+	\caption[Morphospace (principal components) plot of morphological diversity in tenrec and golden mole skulls.]
+		{Principal components plots of the morphospaces occupied by tenrecs (triangles, n=31 species) and golden moles (circles, n=12 species) for the skulls in dorsal (top left), ventral (top right) and lateral (bottom left) views.
+Each point represents the average skull shape of an individual species.
+Axes are principal component 1 (PC1) and principal component 2 (PC2) of the average scores from principal components analyses of mean Procrustes shape coordinates for each species.}
+	\label{fig:threePCA}
+	\end{figure}
 %--------------------------
@@
 First, we compared the position of each Family within the morphospace plots.
-Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001 ), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72 , p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001 ) skull morphospaces,  indicating that the Families have very different, non-overlapping cranial and mandible morphologies (REF PCA figure).
+Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001 ), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72 , p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001 ) skull morphospaces,  indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure \ref{threePCA}.
 
@@
 %----------------------------------------
-%Results table: I changed the format to make it fit better
+%Results table
 
@@
 \subsection{Discussion}
+%Could change this to conclusions
+	Tenrecs are often cited as an example of a mammalian group with high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}.
+They are also more ecologically diverse than their closest relatives \citep{Soarimalala2011, Bronner1995} so we predicted that they would be more morphologically diverse than golden moles.
+However, our results do not support our original prediction, highlighting the importance of quantitative tests of perceived morphological patterns.
+
+	In our full analysis, tenrecs only had higher morphological diversity than golden moles when the skulls were measured in lateral view (Table \ref{tab:diversity}).
+There was no difference in morphological diversity when we analysed the skulls in dorsal or ventral views.
+This is most likely due to our choice of landmarks.
+The two outline curves in lateral view (Figure REF) emphasise morphological variation in the back and top of the skulls.
+These curves summarise overall shape variation but they do not identify clear anatomical differences because they are defined by relative features rather than homologous structures \citep{Zelditch2012}.
+Therefore, high morphological diversity in tenrecs when analysed in this view may not indicate biologically or ecologically relevant variation.
+	These lateral aspects of the skull morphology were not visible in the dorsal and ventral photographs so they could not be included in those analyses.
+In contrast, our landmarks in the dorsal, and particularly ventral, views focus on morphological variation in the overall outline shape of the sides of the skull and palate (Figure REF).
+The result that tenrecs are no more diverse than golden moles in these areas makes intuitive sense: most tenrecs have broad, non-specialised diets \citep{Olson2013} so there is no obvious functional reason why they should have particularly diverse palate morphologies.
+	The different results for our analysis of lateral skull morphologies compared to dorsal and ventral views highlight the importance of using multiple approaches when studying 3D morphological shape using 2D geometric morphometrics techniques \citep{Arnqvist1998}.
+
+	In addition to the differences among the three skull views, our results indicate that, in skulls at least, the overall morphological diversity within tenrecs is not as large as is often assumed \citep[e.g.][]{Eisenberg1969, Olson2013}.
+Studies of morphological variation are sensitive to the sampling used.
+If a particular morphotype is over-represented then the similarities among those species will reduce the overall morphological variation within the group \citep{Foote1991}.
+This appears to be the case for our data; it was only when we included a sub-sample of \textit{Microgale} tenrecs that we found higher morphological diversity in tenrecs compared to golden moles across all three skull analyses (Table \ref{tab:diversity}).
+	While there are clear physical differences among Family members \citep{Olson2013, Eisenberg1969}, the majority of tenrecs are very morphologically similar \citep{Jenkins2003} so morphological diversity in the Family as a whole is not as large as it first appears.
+Of course our results are based on skull shape only and analyses of other morphological traits may produce different results, but they do provide an insight into the differences between subjective and quantitative assessments of morphological diversity.
+
+	\subsection{Caveats} %May need to reduce this one down, and probably take it out of its own separate section
+
+	As highlighted above, landmark choice and placement will inevitably influence the results of a geometric morphometrics study.
+Our interest in broad-scale, cross-taxonomic comparisons of cranial morphology constrained our choice of landmarks to those that could be accurately identified in many different species \citep[e.g.][]{Ruta2013, Goswami2011, Wroe2007}.
+In contrast, studies that use skulls to characterise morphological variation within species \citep[e.g.][]{Blagojevic2011, Bornholdt2008} or to delineate species boundaries within a clade \citep[e.g.][]{Panchetti2008} tend to focus on more detailed, biologically homologous landmarks \citep{Zelditch2012}.
+Repeating our analyses with a narrower taxonomic focus may give greater insight into the specific morphological differences among subgroups of tenrecs and golden moles.
+
+	The goal of our study was to quantify morphological variation in tenrecs instead of relying on subjective assessments of their high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}.
+However, it is difficult to quantify overall morphological diversity because any study is inevitably constrained by its choice of specific traits \citep{Roy1997}.
+Variation in skull shape is only one aspect of overall morphology.
+Quantifying variation in other morphological traits could yield different patterns.
+Therefore future work should extend our approach beyond skulls to gain a more complete understanding of the overall morphological diversity of tenrecs and golden moles.
 %**********************************
 \section{Conclusions}
-
+	We have presented the first quantitative investigation of morphological diversity in tenrecs.
+Our results indicate that, overall, tenrec skulls are not more morphologically diverse than golden moles and that similarities among the species rich \textit{Microgale} tenrecs mask signals of higher morphological diversity among the rest of the Family.
+Of course the results presented here are restricted to just one axis of morphological variation and further analysis of other traits is required.
+However, our findings provide a foundation for future investigations and represent a significant step towards a more quantitative understanding of patterns of morphological and evolutionary diversity in tenrecs.
 %*******************************
-\section{Acknowledgements}
-
+\section{Acknowledgements} %PeerJ have a separate section for funding acknowledgements
+	We thank Thomas Guillerme, Fran\c{c}ois Gould and the members of NERD club for their insightful discussions and comments.
+Thank you to museum staff and curators for facilitating our access to their collections: Leona Leonard and Nigel Monaghan (Natural History Museum, Ireland), Roberto Portela Miguez and Paula Jenkins (Natural History Museum, London), Esther Langan (Smithsonian Institute), Eileen Westwig (American Museum of Natural History), Judy Chupasko (Museum of Comparative Zoology) and Bill Stanley and Steve Goodman (Field Museum).
 %********************************

### 2015-01-27 analyses/diversity_PCAplots_3panel.r

@@ -1,0 +1,255 @@
+
+  #Script to make a 3-panel PCA plot of each data set for my paper
+    #Updated to have the families idenfied as different symbols instead of different colours
+  
+  #Analysis code is exactly the same as the diversity_twofamily_cent_dist script except that the
+  #data objects are re-named so I can have all four data sets within the one R session to plot the graphs together
+
+#-----------------------------------------------------------------------------------
+
+library(geomorph)
+library(vegan)
+library(boot)
+
+source("C:/Users/sfinlay/Desktop/Diversity/functions/Morpho_diversity_functions.r")
+
+########################################################
+#READ IN DATA; directory will change for each data set
+  #Re-name the objects with skdors, skvent etc to distinguish between them
+########################################################
+  setwd("C:/Users/sfinlay/Desktop/Diversity/data")
+#SkDors data
+
+#1) Landmarks
+#landmarks + curves file with the control lines removed
+  skdors.land <- readland.tps(file="skdors/Skdors_16_12_13_10landmarks+4curves_edited.TPS")
+
+#2) Sliders
+#edited sliders file (top 2 rows removed and the words before slide after put in instead
+  skdors.curves <- as.matrix(read.table("skdors/Skdors_16_12_13_10landmarks+4curves_sliders_edited.NTS", header=TRUE))
+
+#3) Taxonomy
+#file that has the correct taxonomy for each of the images
+  skdors.taxa <- read.csv ("skdors/Skdors_16_12_13_10landmarks_images+specimens.csv" , header=T)
+
+#4) Specimens to remove
+  #Null
+#--------------------------------------------------------
+#SkLat data
+
+#1) Landmarks
+  sklat.land <- readland.tps(file="sklat/SkLat_08_11_13_9landmarks_2curves_edited.TPS")
+#2) Sliders
+  sklat.curves <- as.matrix(read.table(file="sklat/SkLat_08_11_13_9landmarks_2curves_sliders_edited.NTS", header=TRUE))
+#3) Taxonomy
+  sklat.taxa <- read.csv("sklat/SkLat_08_11_13_Specimens+images.csv", header=TRUE)
[…]

### 2015-01-27 paper/Diversity_MS.tex
Full manuscript draft

@@
 %-----------------------------------------
-%Title page? NB PeerJ say that they don't need a title page
+%Current title page 
+%NB PeerJ don't want a title page: just the author details but I haven't figured out how to do that without losing the formatting of the rest of the manuscript
+%I may need to get rid of the lists of tables and figures at the end: they want titles and legends to be on the same page as the figure/table
 %----------------------------------------
-\title{}
+\title{Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives}
 
@@
 %****************************************************
+%Abstract
+%Peer J wants the abstract as a separate document
 
-%Abstract in a separate document for PeerJ
 %****************************************************
@@
 	The methods we used involved several steps of data collection, geometric morphometrics analyses and comparisons of morphological diversity.
+These included i) data collection, ii)geometric morphometric analyses and iii)estimating morphological diversity.
 For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.
+
 %Methods flow chart
@@
 
-\subsubsection{Landmark placement on images}
-
 	We used a combination of landmark and semilandmark analysis approaches to assess the shape variability in skull.
@@
 
-	Figure (REF) depicts that landmarks and curves which we used for each of the sets of photographs.
+	Figure \ref{fig:landmarks} depicts that landmarks and curves which we used for each of the sets of photographs.
 For landmarks which are defined by dental structures, we used published dental sources \citep{Repenning1967, Eisenberg1969, Nowak1983, MacPhee1987, KnoxJones1992, Davis1997, Querouil2001, Nagorsen2002, Wilson2005, Goodman2006, Karatas2007, Hoffmann2008, Asher2008,  Muldoon2009, Lin2010} where available to identify the number and type of teeth in each species.
@@
 %****************************************************	
-	%Put the landmark tables into supplementary
-
-	%Add the landmarks picture: three skulls together
+	%Landmark pictures: 3 skulls together	
+	\begin{figure}[!htbp]
+		\centering
+		\includegraphics[width=1\linewidth]{figures/skdors+skvent+sklat_BW.png}
+		\caption[Skulls: dorsal, ventral and lateral landmarks]
+		{Landmarks (numbered points) and curves (outlines) for the skulls in dorsal,ventral and lateral view.
+See the supplementary material for detailed landmark descriptions.
+The skulls are two different specimens of \textit{Potamogale velox} (otter shrew tenrec), museum accession numbers AMNH 51327 (dorsal picture) and BMNH 1934.6.16.2 (ventral and lateral pictures).
+}
+		\label{fig:landmarks}
+	\end{figure}
 
 	%Maybe put morphometrics error checking into the supplementary as well?
+	%Put the landmark tables into supplementary
 %***************************************************
@@
 First, we compared the position of each Family within the morphospace plots.
-Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001 ), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72 , p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001 ) skull morphospaces,  indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure \ref{threePCA}.
+Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001 ), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72 , p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001 ) skull morphospaces,  indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure \ref{fig:threePCA}.
 

### 2015-01-27 paper/Diversity_supplementary.tex
Full manuscript draft

\documentclass[12pt,a4paper]{article}
\usepackage{enumerate} 	% put in numbers or bullet points
\usepackage{setspace}	% line spacing					
\usepackage{authblk}	% For author affiliations
\usepackage{graphicx} 	% For adding pictures
\usepackage{pdflscape}	% for landscape pages
\usepackage{mathtools}	% For equations etc.
\usepackage[osf]{mathpazo} 
\usepackage{float}		
\floatstyle{plaintop} 	% Force table captions to go above the table
\usepackage{longtable}
\usepackage[margin ={2cm, 2cm, 2cm, 2cm}]{geometry}
\usepackage[round]{natbib}
%\setcounter{secnumdepth}{0} % removes numbers from section headings
\raggedright 			% justify the text on the left only
\pagenumbering{arabic}
\linespread{1.6}

\begin{document}

\title{
       Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives.\\
       \bigskip
       Supplementary Material }
\author{Sive Finlay and Natalie Cooper}
\date{}
\maketitle
%I could take more out of the main paper and add it to here
%---------------------------------------------------------
%Landmarks 
%---------------------------------------------------------
\section{Landmark descriptions}
	The information below provides further details about the landmarks we used to summarise morphological shape in tenrec and golden mole skulls. Landmark numbers and curve descriptions refer to Figure 2 in the main paper. One of us (SF) placed all of the landmarks on each picture.

\subsection{Skulls: dorsal view}
	Most of our landmarks in this view are relative (type 3) points which represent overall morphological shape but not necessarily homologous biological features \citep{Zelditch2012}. We placed ten landmarks and drew four semilandmark curves to represent the shape of both the braincase (posterior) and nasal (anterior) area of the skulls. Table \ref{tab:skdors} describes how we defined the landmarks and outline curves for our images of skulls in dorsal view.

%Table with skdors landmark descriptions
\begin{table}[h]
	\caption[Skulls: dorsal landmarks]
		{Descriptions of the landmarks (points) and curves (semilandmarks) for the skulls in dorsal view} 
	\input{tables/skdors.landmarks}
	\label{tab:skdors}
\end{table}
%--------------------------------------------------------------

\subsection{Skulls: ventral view}
	Most of the landmarks in this view are concentrated around the dentition and palate of the animals. We identified 13 landmarks and drew one outline curve (resampled to 60 semilandmark points) around the back of the skull between landmarks 12 and 13. The high variability of our species' basi-cranial regions and difficulties associated with identifying developmentally or functionally homologous points precluded designation of additional landmarks towards the back of the skulls. Table \ref{tab:skvent} outlines the descriptions of the landmarks we used for the ventral skull photos.

% Skulls ventral landmarks
\begin{table}[!htb] 
\caption[Skulls: ventral landmarks]
		{Descriptions of the landmarks (points) and curves (semilandmarks) for the skulls in ventral view.} 
\input{tables/skvent.landmarks}
\label{tab:skvent}
\\
*This curve does not necessarily trace homologous features because of the variation in the position of the foramen magnum.
\end{table}

%------------------------------------------------------
\newpage
\subsection{Skulls: lateral view}
	We placed nine landmarks on the photographs of skulls in lateral view and also drew two semilandmark curves to represent the shape of the back of the skull (between landmarks 7 and 8, re-sampled to 20 semilandmark points) and the top of the skull (between landmarks 8 and 1, re-sampled to 15 semilandmark points). Table \ref{tab:sklat} describes our definitions for each of the landmark points.
	If specimens were damaged on their right side we reflected photographs of the left lateral side of the skull so that all the images were in the same orientation.

% Skulls lateral landmarks
\begin{table}[!htb]
\caption[Skulls: lateral landmarks]
		{Descriptions of the landmarks (points) and curves (semilandmarks) for the skulls in lateral view.} 
\input{tables/sklat.landmarks}
\label{tab:sklat}
\end{table}
%-------------------------------------------
\bibliographystyle{sysbio} 
\bibliography{refs_paper} 
\end{document}

### 2015-01-27 analyses/diversity_twofamily.r
Added data, code and output

@@ -1,0 +1,304 @@
+#27/01/15
+
+  #Morphological disparity calculations
+    #Calculate disparity as based on euclidean distances from the centroid for each family
+      #Compare the dispersion of tenrecs and golden moles around their average skull shapes
+
+  #Note that this script can be used for each of the three analyses (skulls in dorsal/ventral/lateral views)
+  #There is also an option to use a reduced data set: subsampling the tenrecs to include just five Microgale species
+    
+
+
+#steps:
+  #1) Read in a clean up raw landmark data
+    #OPTIONS; choices depending on the analysis
+  #2) Procrustes superimposition of tenrecs and golden moles
+  #3) Find the average Procrustes shape coordinates for each species
+  #4) PCA of the shape coordinates
+  #5) Select PC axes that account for 95% of the variation
+  #6) Calculate diversity based on distances from the centroid
+
+library(geomorph)
+library(vegan)
+library(plotrix)
+
+source("C:/Users/sfinlay/Desktop/Diversity/functions/Morpho_diversity_functions.r")
+
+setwd("C:/Users/sfinlay/Desktop/Diversity/data/")
+
+#######################
+#Read in the data: 3 views of skulls
+#################
+#SkDors
+    #1) Landmarks
+      #land <- readland.tps(file="skdors/Skdors_16_12_13_10landmarks+4curves_edited.TPS")
+    #2) Sliders
+      #curves <- as.matrix(read.table("skdors/Skdors_16_12_13_10landmarks+4curves_sliders_edited.NTS", header=TRUE))
+    #3) Taxonomy
+      #taxa <- read.csv ("skdors/Skdors_16_12_13_10landmarks_images+specimens.csv" , header=T)
+    #4) Specimens to remove
+      #Null
+
+#-----------------------------------------------------
+#SkVent
+  #1) Landmarks
+    #land <- readland.tps(file="skvent/SkVent_30_10_13_13landmarks+1curve_edited.TPS")
+  #2) Sliders
+    #curves <- as.matrix(read.table(file="skvent/SkVent_1skull_13landmarks+1curve_sliders_edited.tps", header=TRUE))     #this is a tps file and the others are nts but it doesn't make a difference
+  #3) Taxonomy
+    #taxa <- read.csv("skvent/SkVent_30_10_13_imagelist+specimens.csv" , header=TRUE)
+  #4) Specimens to remove
+    #rem <- read.csv("skvent/SkVent_remove_spec.csv", header=T)
+
[…]

### 2015-01-27 paper/Diversity_MS.tex
Edited manuscript

@@
 
+%This is the abstract from my thesis
+
+	%Patterns of morphological diversity (the variety of physical form) have important implications for our understanding of species ecology and evolution.
+Some clades such as cichlid fish and anole lizards are known for their high morphological diversity.
+Studying these groups can provide insights into the processes that led to the evolution of this exceptional diversity.
+	%Morphological diversity is often studied qualitatively.
+However, to truly understand the evolution of diversity, it is important to take a quantitative approach instead of relying on subjective, qualitative assessments.
+Here, we present a quantitative analysis of morphological diversity in a Family of small mammals, the tenrecs (Afrosoricida, Tenrecidae).
+	%Tenrecs are often cited as an example of an exceptionally morphologically diverse group.
+However, this assumption has not been tested quantitatively.
+We use geometric morphometric analyses of skull shape to test whether tenrecs are more morphologically diverse than their closest relatives, the golden moles (Afrosoricida, Chrysochloridae).
+Tenrecs occupy a wider range of ecological niches than golden moles so we predicted that they would be more morphologically diverse.
+	%Contrary to our expectations, We found that tenrec skulls are only more morphologically diverse than golden moles when measured in lateral view.
+Furthermore, similarities among the species-rich \textit{Microgale} tenrec Genus appear to mask higher morphological diversity in the rest of the Family.
+These results reveal new insights into the morphological diversity of tenrecs and highlight the importance of using quantitative methods to test qualitative assumptions about patterns of morphological diversity.
+
 %****************************************************
@@
 Therefore, it is important to quantify patterns of morphological diversity in tenrecs to gain an insight into their evolution.
-My thesis is the first study to address this issue.
 
@@
 Greater ecological variety is often (though not always) correlated with higher morphological diversity \citep{Losos2010a}.
+	However, our results reveal that, in skulls at least, morphological diversity in tenrecs is not as great as it first appears.
 
-	%Finish off this introduction
+	%Might need more to finish off the introduction?
 %************************************
@@
 
-%Overview section: data, geometric morphometrics, measuring diversity
-
-	The methods we used involved several steps of data collection, geometric morphometrics analyses and comparisons of morphological diversity.
-These included i) data collection, ii)geometric morphometric analyses and iii)estimating morphological diversity.
+	The methods we used involved several steps of i) data collection, ii) geometric morphometric analyses and iii) estimating morphological diversity.
 For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.
@@
 	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}. 
-	Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull pictures along with the mandibles \citep{Finlay2013m}.
-Copyright restrictions from the other museums prevent public sharing of their images however they are available on request.
+	Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull pictures.
+Copyright restrictions from the other museums prevent public sharing of their images but they are available on request.
 
@@
 
-	We used a combination of landmark and semilandmark analysis approaches to assess the shape variability in skull.
+	We used a combination of landmark and semilandmark analysis approaches to assess the shape variability in the skulls.
 We used the TPS software suite \citep{Rohlf2013} to digitise landmarks and curves on the photos.
-We set the scale on each image individually to standardise for the different camera heights that I used when photographing my specimens.
+We set the scale on each image individually to standardise for the different camera heights used when photographing the specimens.
 We created separate data files for each of the three morphometric analyses (skulls in dorsal, ventral and lateral views).
@@
 Some specimens were too damaged to use in particular views so there were a different total number of images for each analysis.
-We photographed 182 skulls in dorsal view (148 tenrecs and 34 golden moles), 173 skulls in ventral view (141 tenrecs and 32 golden moles) and 171 skulls in lateral view (140 tenrecs and 31 golden moles).
+Our final data sets included photographs of 182 skulls in dorsal view (148 tenrecs and 34 golden moles), 173 skulls in ventral view (141 tenrecs and 32 golden moles) and 171 skulls in lateral view (140 tenrecs and 31 golden moles).
 
+%Maybe move this to the supplementary?
 	When using semilandmark approaches there is a potential problem of over - sampling: simpler structures will require fewer semilandmarks to accurately represent their shape  \citep{MacLeod2012}.
@@
 We calculated the length of each re-sampled curve as a percentage of the total length of the curve and then found the average percentage length for that reduced number of semilandmark points across all of the specimens in my test file.
-We continued this process until I found the minimum number of points that gave a curve length which was at least 95\% accurate.
+We continued this process until we found the minimum number of points that gave a curve length which was at least 95\% accurate.
 We repeated these curve-sampling tests for each analysis to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.
@@
 
-	%Maybe put morphometrics error checking into the supplementary as well?
-	%Put the landmark tables into supplementary
 %***************************************************
@@
 We combined the landmarks and taxonomic identification files into a single morphometrics data object and carried out all further analyses in R version 3.1.1 \citep{Team2014}.
-Data and code for all of our analyses is available on GitHub (REF to paper repository).
+Data and code for all of our analyses is available on GitHub \citep{Finlay2015c}.
 
 	At this stage, we either used the full data set (31 species of tenrec and 12 species of golden mole) or a reduced data set with just 17 species of tenrec (Figure \ref{fig:flow}).
-We created this reduced data set because the majority of tenrec species (19 out of 31 in my data) belong to the \textit{Microgale} (shrew-like) Genus that has relatively low morphological diversity \citep{Soarimalala2011, Jenkins2003}.
+We created this reduced data set because the majority of tenrec species (19 out of 31 in our data) belong to the \textit{Microgale} (shrew-like) Genus that has relatively low morphological diversity \citep{Soarimalala2011, Jenkins2003}.
 This may mask signals of higher morphological diversity among other tenrecs.
@@
 If this is true, when we randomly assign the group identity of each species (i.e.
-shuffle the "tenrec" and "golden mole" labels) and then re-compare the morphological diversity of the two groups, there will be no significant difference between these results and those obtained when the species are assigned to the correct groupings.
+shuffle the "tenrec" and "golden mole" labels) and then re-compare the morphological diversity of the two groups, there would be no significant difference between these results and those obtained when the species are assigned to the correct groupings.
 	We performed this shuffling procedure (random assignation of group identity) 1000 times and calculated the difference in morphological diversity between the two groups for each permutation.
@@
 %*********************************
-\section{Results and Discussion} %PeerJ asks for these two sections to go together
-
-\subsection{Results}
+\section{Results} %PeerJ lists results and discussion together but I think it makes more sense to keep them separate
 	Figure \ref{fig:threePCA} depicts the morphospaces defined by the first two principal component (PC) axes from our principal components analyses (PCAs) of skull and mandible morphologies.
@@
 %--------------------------
-	To compare morphological diversity in the two families, we used the PC axes which accounted for 95\% of the cumulative variation in each of the skull analyses: dorsal (n=6 axes), ventral (n=7 axes) and lateral (n=7 axes).
+	To compare morphological diversity in the two Families, we used the PC axes which accounted for 95\% of the cumulative variation in each of the skull analyses: dorsal (n=6 axes), ventral (n=7 axes) and lateral (n=7 axes).
 First, we compared the position of each Family within the morphospace plots.
@@
 %----------------------------------
-\subsection{Discussion}
-%Could change this to conclusions
+\section{Discussion}
+%Could move this paragraph to the conclusions
 	Tenrecs are often cited as an example of a mammalian group with high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}.
@@
 This is most likely due to our choice of landmarks.
-The two outline curves in lateral view (Figure REF) emphasise morphological variation in the back and top of the skulls.
+The two outline curves in lateral view (Figure \ref{fig:landmarks}) emphasise morphological variation in the back and top of the skulls.
 These curves summarise overall shape variation but they do not identify clear anatomical differences because they are defined by relative features rather than homologous structures \citep{Zelditch2012}.
@@
 	These lateral aspects of the skull morphology were not visible in the dorsal and ventral photographs so they could not be included in those analyses.
-In contrast, our landmarks in the dorsal, and particularly ventral, views focus on morphological variation in the overall outline shape of the sides of the skull and palate (Figure REF).
+In contrast, our landmarks in the dorsal, and particularly ventral, views focus on morphological variation in the overall outline shape of the sides of the skull and palate (Figure \ref{fig:landmarks}).
 The result that tenrecs are no more diverse than golden moles in these areas makes intuitive sense: most tenrecs have broad, non-specialised diets \citep{Olson2013} so there is no obvious functional reason why they should have particularly diverse palate morphologies.
 The different results for our analysis of lateral skull morphologies compared to dorsal and ventral views highlight the importance of using multiple approaches when studying 3D morphological shape using 2D geometric morphometrics techniques \citep{Arnqvist1998}.
+%I moved this paragraph up instead of leaving it in a separate caveats section	
+	Landmark choice and placement will inevitably influence the results of a geometric morphometrics study.
+Our interest in broad-scale, cross-taxonomic comparisons of cranial morphology constrained our choice of landmarks to those that could be accurately identified in many different species \citep[e.g.][]{Ruta2013, Goswami2011, Wroe2007}.
+In contrast, studies that use skulls to characterise morphological variation within species \citep[e.g.][]{Blagojevic2011, Bornholdt2008} or to delineate species boundaries within a clade \citep[e.g.][]{Panchetti2008} tend to focus on more detailed, biologically homologous landmarks \citep{Zelditch2012}.
+Repeating our analyses with a narrower taxonomic focus may give greater insight into the specific morphological differences among subgroups of tenrecs and golden moles.
 
@@
 	While there are clear physical differences among Family members \citep{Olson2013, Eisenberg1969}, the majority of tenrecs are very morphologically similar \citep{Jenkins2003} so morphological diversity in the Family as a whole is not as large as it first appears.
-Of course our results are based on skull shape only and analyses of other morphological traits may produce different results, but they do provide an insight into the differences between subjective and quantitative assessments of morphological diversity.
-
-	\subsection{Caveats} %May need to reduce this one down, and probably take it out of its own separate section
-
-	As highlighted above, landmark choice and placement will inevitably influence the results of a geometric morphometrics study.
-Our interest in broad-scale, cross-taxonomic comparisons of cranial morphology constrained our choice of landmarks to those that could be accurately identified in many different species \citep[e.g.][]{Ruta2013, Goswami2011, Wroe2007}.
-In contrast, studies that use skulls to characterise morphological variation within species \citep[e.g.][]{Blagojevic2011, Bornholdt2008} or to delineate species boundaries within a clade \citep[e.g.][]{Panchetti2008} tend to focus on more detailed, biologically homologous landmarks \citep{Zelditch2012}.
-Repeating our analyses with a narrower taxonomic focus may give greater insight into the specific morphological differences among subgroups of tenrecs and golden moles.
-
 	The goal of our study was to quantify morphological variation in tenrecs instead of relying on subjective assessments of their high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}.
@@
 Therefore future work should extend our approach beyond skulls to gain a more complete understanding of the overall morphological diversity of tenrecs and golden moles.
+	%I combined the paragraph above within the discussion (previously it was part of a separate caveats section)
+	While recognising these limitations, our results provide valuable insights into the differences between subjective and quantitative assessments of morphological diversity. 
 %**********************************

### 2015-01-27 paper/Diversity_MS.tex
Fixed first page issues

--- 2015-01-27 paper/Diversity_MS.tex
@@
 %----------------------------------------
-\title{Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives}
 
-\author{Sive Finlay$^{1,2}$ and Natalie Cooper$^{1,2,*}$}
-\affiliation{\noindent{\footnotesize
-$^1$ School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\ 
-$^2$ Trinity Centre for Biodiversity Research, Trinity College Dublin, Dublin 2, Ireland.\\
-$^*$Corresponding author: ncooper@tcd.ie; Zoology Building, Trinity College Dublin, Dublin 2, Ireland.\\ Tel: +353 1 896 1926.\\}}
-\date{}	% To give blank date
-
-\runninghead{Cranial morphological diversity in tenrecs }
-
-\keywords{geometric morphometrics, golden moles, morphological diversity, tenrecs}
 %---------------------------------------------------------------
@@
 
-\mstitlepage			% Instead of \maketitle you can use the nice template to get it looking like a manuscript
 \parindent=1.5em		% Changes paragraph indenting so it's not so big
 \addtolength{\parskip}{.3em} % Changes spacing between sections so it's smaller
+
+\noindent
+\textsc{Sive Finlay$^{1,2}$ and Natalie Cooper$^{1,2,*}$}\\
+
+\noindent
+$^1$ School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\ 
+\noindent
+$^2$ Trinity Centre for Biodiversity Research, Trinity College Dublin, Dublin 2, Ireland.\\
+\noindent
+$^*$Corresponding author: Natalie Cooper; ncooper@tcd.ie; Zoology Building, Trinity College Dublin, Dublin 2, Ireland. Tel: +353 1 896 1926.\\
+
+\newpage
 %****************************************************
@@
 	We thank Thomas Guillerme, Fran\c{c}ois Gould and the members of NERD club for their insightful discussions and comments.
-Thank you to museum staff and curators for facilitating our access to their collections: Leona Leonard and Nigel Monaghan (Natural History Museum, Ireland), Roberto Portela Miguez and Paula Jenkins (Natural History Museum, London), Esther Langan (Smithsonian Institute), Eileen Westwig (American Museum of Natural History), Judy Chupasko (Museum of Comparative Zoology) and Bill Stanley and Steve Goodman (Field Museum).
+Thank you to museum staff and curators for facilitating our access to their collections: Leona Leonard and Nigel Monaghan (Natural History Museum, Ireland), Roberto Portela Miguez and Paula Jenkins (Natural History Museum, London), Esther Langan (Smithsonian Institute NMNH), Eileen Westwig (American Museum of Natural History), Judy Chupasko (Museum of Comparative Zoology) and Bill Stanley and Steve Goodman (Field Museum).
 %********************************

### 2015-01-28 paper/Diversity_supplementary.tex

@@
 \usepackage[round]{natbib}
+\usepackage{hyperref} %need this for url references
+
 %\setcounter{secnumdepth}{0} % removes numbers from section headings
@@
 %-------------------------------------------
+\section{\normalfont{Potential morphometrics errors}}
+
+	While 2D methods are an accepted means of comparing morphological shape \citep[e.g.][]{Adams2004, Mitteroecker2009}, particularly for comparing skull morphologies of small mammals \citep[e.g.][]{Cardini2003, Panchetti2008, White2008, Barrow2008, Scalici2011}, the inherent discrepancies associated with comparing three dimensional objects using two dimensional pictures can introduce some potential problems of possible image distortion \citep{Arnqvist1998}.
+Similarly, human error with how landmarks are positioned on specimens could also introduce noise into further analyses.
+
+	In contrast to detailed intraspecific work \citep[e.g.][]{Bornholdt2008, Blagojevic2011}, photographic or landmark placement errors are unlikely to be significant in our interspecific study since one would expect that the morphological variation among species is large enough to  be detected as a signal above any background noise associated with methodological error \citep{Arnqvist1998}.
+Nevertheless, it is still important to assess measurement error in a morphometric data set to increase confidence in the outcome of final analyses.
+	We identified two possible sources of morphometric measurement error: specimen orientation and placement of landmarks.
+
+	Variation in the orientation of specimens for photography is one of the main sources of error in 2D morphometric studies \citep{Adriaens2007}.
+If specimens are not placed on a flat plane or in a consistent position relative to the camera, areas of the object which are tilted towards the camera will appear to be larger than in reality, distorting any subsequent morphometric analyses of the shape.
+	One of us (SF) placed the landmarks on each set of pictures so inter-observer variation in landmark placement is not an issue for our study.
+However, repeatability and reliability of our choice of landmarks could affect the final results of the analyses \citep{Arnqvist1998}.
+
+	To measure potential orientation error, we photographed the skulls (dorsal, ventral and lateral views) of each specimen three times, cycling through the photos so that the specimen was removed and re-positioned before every shot \citep{Viscosi2011}.
+	We used a subset of the ventral skull images to test for two sources of error: specimen orientation and landmark placement error \citep{Arnqvist1998, Barrow2008}.
+Of the specimens which we photographed three times, we chose a random subset of seven skulls from four different Families: three tenrecs and single representatives of shrews, moles, hedgehogs and golden moles.
+We copied these images and placed landmarks on three copies of each image to compare variation in landmark placement within each orientation.
+This gave nine replicates of each skull: three separate photos, and three copies of each of those photos.
+As before, we ran a general Procrustes alignment \citep{Rohlf1993} of the specimens, calculated the average shape values for each skull (average of all nine pictures) and used these values for a principal components (PC) analysis.
+
+	We used a linear mixed effects model to model the shape variation (first PC axis) associated with specimen (fixed effect) and two nested random effects: photo identity nested within specimen and image replicate nested within each photograph.
+This nested approach was necessary to deal with the hierarchical nature of our data subset: three photos of every specimen and three replicates of each of those images.
+We ran the test using the lmer function in the lme4 package \citep{Bates2014}.
+
+	We found that specimen orientation and landmark placement have negligible effects on the overall shape variation between different skulls: the random effect variables of photo identify and image replicate explained less than 0.0001 \% of the overall shape variation among different skulls.
+Therefore, we are confident that shape variation among the specimens in the rest of the analyses reflects true morphological differences rather than methodological error.
+
 \bibliographystyle{sysbio} 

### 2015-01-28 paper/Diversity_MS.tex
Edits to intorduction and preamble

@@
 \documentclass[12pt,a4paper]{article}
-\usepackage{enumerate} 	% put in numbers or bullet points
-\usepackage{setspace}	% line spacing					
-\usepackage{authblk}	% For author affiliations
-\usepackage{graphicx} 	% For adding pictures
+\usepackage{enumerate} 	
+\usepackage{setspace}						
+\usepackage{authblk}	
+\usepackage{graphicx} 	
+\usepackage[nomarkers, nolists]{endfloat} 
+\usepackage{pdflscape}	
+\usepackage{mathtools}	
+\usepackage[osf]{mathpazo} 
+\usepackage{fixltx2e}	
+\usepackage{lineno}    	
+\usepackage{hyperref}
+\usepackage[round]{natbib} 
+\usepackage{setspace}
 
-\usepackage[nomarkers]{endfloat} %Figures and tables at the end of the document
-\usepackage{pdflscape}	% for landscape pages
-\usepackage{mathtools}	% For equations etc.
-\usepackage[osf]{mathpazo} % palatino font package
-\usepackage{fixltx2e}	% includes subscripts
-\usepackage{ms}     	% load the manuscript style template - may need to change this for PeerJ
-\usepackage{hyperref} %need this for url references
+\setcounter{secnumdepth}{0} 
+\raggedright 			
+\pagenumbering{arabic}	
+\linenumbers
 
-\setcounter{secnumdepth}{0} % removes numbers from section headings
-\raggedright 			% justify the text on the left only
-\pagenumbering{arabic}	% Page numbers
-
-\usepackage[round]{natbib} % author-year citations in round brackets
-
-%-----------------------------------------
-%Current title page 
-%NB PeerJ don't want a title page: just the author details but I haven't figured out how to do that without losing the formatting of the rest of the manuscript
-%I may need to get rid of the lists of tables and figures at the end: they want titles and legends to be on the same page as the figure/table
-%----------------------------------------
-
-%---------------------------------------------------------------
 % Start of document
 \begin{document}
-\modulolinenumbers[1] 	% Line numbering on every line
 
-\parindent=1.5em		% Changes paragraph indenting so it's not so big
-\addtolength{\parskip}{.3em} % Changes spacing between sections so it's smaller
+\parindent=1.5em		
+\addtolength{\parskip}{.3em} 
+\doublespace
 
+% Title page
 \noindent
@@
 
-\newpage
-%****************************************************
-%Abstract
-%Peer J wants the abstract as a separate document
+% Abstract
 
-%This is the abstract from my thesis
+	% Morphological diversity is often studied qualitatively.
+However, to truly understand the evolution of exceptional diversity, it is important to take a quantitative approach instead of relying on subjective, qualitative assessments.
+Here, we present a quantitative analysis of morphological diversity in a Family of small mammals, the tenrecs (Afrosoricida, Tenrecidae).
 
-	%Patterns of morphological diversity (the variety of physical form) have important implications for our understanding of species ecology and evolution.
-Some clades such as cichlid fish and anole lizards are known for their high morphological diversity.
-Studying these groups can provide insights into the processes that led to the evolution of this exceptional diversity.
-	%Morphological diversity is often studied qualitatively.
-However, to truly understand the evolution of diversity, it is important to take a quantitative approach instead of relying on subjective, qualitative assessments.
-Here, we present a quantitative analysis of morphological diversity in a Family of small mammals, the tenrecs (Afrosoricida, Tenrecidae).
-	%Tenrecs are often cited as an example of an exceptionally morphologically diverse group.
+	% Tenrecs are often cited as an example of an exceptionally morphologically diverse group.
 However, this assumption has not been tested quantitatively.
 We use geometric morphometric analyses of skull shape to test whether tenrecs are more morphologically diverse than their closest relatives, the golden moles (Afrosoricida, Chrysochloridae).
-Tenrecs occupy a wider range of ecological niches than golden moles so we predicted that they would be more morphologically diverse.
-	%Contrary to our expectations, We found that tenrec skulls are only more morphologically diverse than golden moles when measured in lateral view.
+Tenrecs occupy a wider range of ecological niches than golden moles so we predict that they will be more morphologically diverse.
+
+	% Contrary to our expectations, We find that tenrec skulls are only more morphologically diverse than golden moles when measured in lateral view.
 Furthermore, similarities among the species-rich \textit{Microgale} tenrec Genus appear to mask higher morphological diversity in the rest of the Family.
@@
 
-%****************************************************
+\newpage
 \section{Introduction}
@@
 	Analysing patterns of morphological diversity has important implications for our understanding of ecological and evolutionary traits.
-For example, from a functional ecology perspective, morphological characteristics of limbs inform us about locomotory style \citep[e.g.][]{Bou1987} and the trophic niches associated with particular dental morphologies affect speciation and diversification rates through time \citep{Price2012}.
-Morphological diversity is also an important aspect of evolutionary patterns such as adaptive radiations and convergent evolution.
-High morphological diversity is a unifying \citep{Losos2010a, Olson2009}, although not defining \citep{Glor2010, Olson2009}, characteristic of adaptive radiations.
-Furthermore, analysing morphological convergences in groups such as freshwater cichlid fish \citep{Muschick2012} and anole lizards \citep{Mahler2013} gives interesting insights into the relative repeatability of evolution \citep{Losos2011}.
+Species morphology can influence niche occupancy and affect speciation and diversification rates through time \citep{Price2012}.
+High morphological diversity is also a unifying \citep{Losos2010a, Olson2009}, although not defining \citep{Glor2010, Olson2009}, characteristic of adaptive radiations.
+Furthermore, analysing morphological convergences in groups such as freshwater cichlid fish \citep{Muschick2012} and anole lizards \citep{Mahler2013} provides insights into the relative repeatability of evolution \citep{Losos2011}.
 
@@
 Studies are inevitably constrained to measure the diversity of specific traits rather than overall morphologies \citep{Roy1997}.
-In addition, our perception of morphological diversity is influenced by the trait being used.
-One study of pterosaurs demonstrated that comparing the diversity of different morphological traits using varying methods produced similar results \citep{Foth2012}.
-However, it remains unclear whether this finding can be applied to all vertebrate groups: in some species, comparing the relative diversity of cranial and limb morphologies may yield different results \citep{Foth2012}.
-Furthermore, linear measurements of morphological traits can restrict our understanding of overall morphological variation.
-A distance matrix of measurements between specific points is unlikely to give a completely accurate representation of a three dimensional structure \citep{Rohlf1993}.
-
-	These are important limitations to consider but geometric morphometric approaches help to overcome some of the issues associated with traditional morphological studies \citep{Adams2004}.
-Morphometric studies based on caliper measurements of particular features can only describe a limited set of distances, ratios and angles which often fail to capture the overall shape of a specific structure \citep{Slice2007}.
-Geometric morphometrics circumvents these issues by using a system of Cartesian landmark coordinates to define anatomical points.
+In addition, our perception of morphological diversity is influenced by the trait being used, and results may depend on the particular trait being analysed \citep{Foth2012}.
+Furthermore, linear measurements of morphological traits can restrict our understanding of overall morphological variation; a distance matrix of measurements among specific points is unlikely to give a completely accurate representation of a three dimensional structure \citep{Rohlf1993}.
+Geometric morphometric approaches can circumvent some of these issues by using a system of Cartesian landmark coordinates to define anatomical points \citep{Adams2004}.
 This method captures more of the true, overall anatomical shape of particular structures \citep{Mitteroecker2009}.
@@
 The Family is comprised of 34 species, 31 of which are endemic to Madagascar \citep{Olson2013}.
-Body masses of tenrecs span three orders of magnitude (2.5 to > 2,000g); a greater range than all other Families, and most Orders, of living mammals \citep{Olson2003}.
+Body masses of tenrecs span three orders of magnitude (2.5 to $>$ 2,000g); a greater range than all other Families, and most Orders, of living mammals \citep{Olson2003}.
 Within this vast size range there are tenrecs which convergently resemble shrews (\textit{Microgale} tenrecs), moles (\textit{Oryzorictes} tenrecs) and hedgehogs \citep[\textit{Echinops} and \textit{Setifer} tenrecs,][]{Eisenberg1969}.
@@
 Therefore, it appears that tenrecs represent an adaptive radiation of species which filled otherwise vacant ecological niches \citep{Soarimalala2011}.
-	The similarities among tenrecs and other small mammals are even more remarkable when you consider their phylogenetic history.
-Tenrecs were originally classified within the general "Insectivora" clade and only molecular studies revealed their true phylogenetic affinities within the Afrotherian mammals \citep{Stanhope1998}.
-Therefore, despite initial appearances, tenrecs are more closely related to elephants, manatees and aardvarks than they are to shrews, moles or hedgehogs.
 
-	Although tenrecs are often cited as an example of both an adaptive radiation and exceptional convergent evolution, these claims have not been investigated quantitatively.
+	Although tenrecs are often cited as an example of both an adaptive radiation and exceptional convergent evolution \citep{Soarimalala2011, Eisenberg1969}, these claims have not been investigated quantitatively.
 There are qualitative similarities among the hind limb morphologies of tenrecs and several other unrelated species with similar locomotory styles \citep{Salton2009} but the degree of morphological similarity has not been established.
@@
 
-	%Might need more to finish off the introduction?
-%************************************
 \section{Materials and Methods}
 
-	The methods we used involved several steps of i) data collection, ii) geometric morphometric analyses and iii) estimating morphological diversity.
+	Our methods involved i) data collection, ii) geometric morphometric analyses and iii) estimating morphological diversity.
 For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.
 
-%Methods flow chart
+% Methods flow chart
 	\begin{figure}[!htbp]
@@
 \subsection{Data collection}
-	One of us (SF) used the collections of five museums: the Natural History Museum, London (BMNH), the Smithsonian Institute Natural History Museum, Washington D.C.
-(SI), the American Museum of Natural History, New York (AMNH), the Museum of Comparative Zoology, Cambridge M.A.
-(MCZ) and the Field Museum of Natural History, Chicago (FMNH).
-We recorded species names as they were written on museum specimen labels and then corrected them to match the taxonomy in Wilson and Reeder's Mammal Species of the World \citeyearpar{Wilson2005}.
-For recently identified species,  which are not included in Wilson and Reeder \citeyearpar{Wilson2005}, we used the taxonomy recorded on the specimen labels.
+	One of us (SF) collected data from five museums: Natural History Museum, London (BMNH), Smithsonian Institute Natural History Museum, Washington D.C.
+(SI), American Museum of Natural History, New York (AMNH), Museum of Comparative Zoology, Cambridge M.A.
+(MCZ) and Field Museum of Natural History, Chicago (FMNH).
+We used the taxonomy in Wilson and Reeder's Mammal Species of the World \citeyearpar{Wilson2005}, except for recently identified species where we used the taxonomy recorded on the specimen labels.
 Wilson and Reeder \citeyearpar{Wilson2005} record 30 species of tenrec but more recent studies indicate that there are now 34 species \citep[][]{Olson2013}.
@@
 This included 31 of the 34 species in the tenrec Family and 12 of the 21 species of golden moles \citep{Wilson2005}.
-	%Left out the points about male/female and adult/juvenile
 
-	We took pictures of the skulls using photographic copy stands consisting of a camera attachment with an adjustable height bar, a flat stage on which to place the specimen and an adjustable light source.
+	We took pictures of the skulls using photographic copy stands.
 To take possible light variability into account, on each day we took a photograph of a white sheet of paper and used the custom white balance function on the camera to set the image as the baseline "white" measurement for those particular light conditions.
@@
 	We photographed the specimens with a Canon EOS 650D camera fitted with a EF 100 mm f/2.8 Macro USM lens.
-We used a remote control (H\"ahnel Combi TF) to take the photos to avoid shaking the camera and distorting the images.
+We used a remote control (H\"ahnel Combi TF) to take the photos to avoid camera shake.
 We photographed the specimens on a black material background with a light source in the top left-hand corner of the photograph.
-We used small bean bags as necessary to hold the specimens in position while being photographed to ensure that they lay in a flat plane relative to the camera and did not tilt in any direction.
+We used small bean bags as necessary to hold the specimens in position while being photographed to ensure that they lay in a flat plane relative to the camera.
 We used the grid-line function on the live-view display screen of the camera to position the specimens in the centre of each image.
 
-	We photographed the skulls in three views: dorsal (top of the cranium), ventral (underside of the skull with the palate roof facing upwards) and lateral (right side of the skull) (Figure \ref{fig:flow}).
-When the right sides of the skulls were damaged or incomplete we photographed the left sides and later reflected the images so that they could be compared to pictures of the right sides \citep[e.g.][]{Barrow2008}.
+	We photographed the skulls in three views: dorsal, ventral and lateral (right side) (Figure \ref{fig:flow}).
+When the right sides of the skulls were damaged or incomplete, we photographed the left sides and later reflected the images so that they could be compared to pictures of the right sides \citep[e.g.][]{Barrow2008}.
 
 	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}. 
-	Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull pictures.
+	Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute Natural History Museum are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull views.
 Copyright restrictions from the other museums prevent public sharing of their images but they are available on request.
@@
 Our final data sets included photographs of 182 skulls in dorsal view (148 tenrecs and 34 golden moles), 173 skulls in ventral view (141 tenrecs and 32 golden moles) and 171 skulls in lateral view (140 tenrecs and 31 golden moles).
-
-%Maybe move this to the supplementary?
-	When using semilandmark approaches there is a potential problem of over - sampling: simpler structures will require fewer semilandmarks to accurately represent their shape  \citep{MacLeod2012}.
-To ensure that we applied a uniform standard of shape representation to each outline segment (i.e.
-that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012}.
-For each data set we chose a random selection of photos of specimens which represented the breadth of the morphological data (i.e.
-specimens from each sub-group of species).
-We drew the appropriate curves on each specimen and over-sampled the number of points on the curves.
-We measured the length of the line and regarded that as the 100\%, true length of that outline.
-We then re-sampled the curves with decreasing numbers of points and measured the length of the outlines.
-We calculated the length of each re-sampled curve as a percentage of the total length of the curve and then found the average percentage length for that reduced number of semilandmark points across all of the specimens in my test file.
-We continued this process until we found the minimum number of points that gave a curve length which was at least 95\% accurate.
-We repeated these curve-sampling tests for each analysis to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.
 
@@
 
+%Maybe move this to the supplementary?
+% NC: Can it just be condensed?
+	When using semilandmark approaches there is a potential problem of over-sampling: simpler structures will require fewer semilandmarks to accurately represent their shape \citep{MacLeod2012}.
+To ensure that we applied a uniform standard of shape representation to each outline segment (i.e.
+that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012}.
+For each data set we chose a random selection of photos of specimens which represented the breadth of the morphological data (i.e.
+specimens from each sub-group of species).
+We drew the appropriate curves on each specimen and over-sampled the number of points on the curves.
+We measured the length of the line and regarded that as the 100\%, true length of that outline.
+We then re-sampled the curves with decreasing numbers of points and measured the length of the outlines.
+We calculated the length of each re-sampled curve as a percentage of the total length of the curve and then found the average percentage length for that reduced number of semilandmark points across all of the specimens in my test file.
+We continued this process until we found the minimum number of points that gave a curve length which was at least 95\% accurate.
+We repeated these curve-sampling tests for each analysis to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.
+
 	After creating the files with the landmarks and semilandmarks placed on each photograph, we used TPSUtil \citep{Rohlf2012} to create "sliders" files that defined which points in the TPS files should be treated as semilandmarks \citep{Zelditch2012}.
@@
 
-	For each analysis, we used the gpagen function in the geomorph package \citep{Adams2013} to run a general Procrustes alignment \citep{Rohlf1993} of the landmark coordinates while sliding the semilandmarks by minimising Procrustes distance \citep{Bookstein1997}.
-We used these Procrustes-aligned coordinates of all specimens to calculate average shape values for each species which we then used for a principal components (PC) analysis with the plotTangentSpace function \citep{Adams2013}.
+	For each analysis, we used the \texttt{gpagen} function in the geomorph package \citep{Adams2013} to run a general Procrustes alignment \citep{Rohlf1993} of the landmark coordinates while sliding the semilandmarks by minimising Procrustes distance \citep{Bookstein1997}.
+We used these Procrustes-aligned coordinates of all specimens to calculate average shape values for each species which we then used for a principal components (PC) analysis with the \texttt{plotTangentSpace} function \citep{Adams2013}.
 We selected the number of principal component (PC) axes that accounted for 95\% of the variation in the data (Figure \ref{fig:flow}) and used these axes to estimate morphological diversity in each Family.
@@
 We define morphological diversity as the mean Euclidean distance (sum of squared differences) between each species and its Family centroid (Figure \ref{fig:centroids}).
-This is summarised in the equation below where \textit{n} is the number of species in the Family, \textit{i} is the number of PC axes and \textit{c} are the average PC scores for each axis (the centroid).
+This is summarised in the equation below where \textit{n} is the number of species in the Family, \textit{i} is the number of PC axes and \textit{c} is the average PC score for each axis (the centroid).
 
@@
 	While recognising these limitations, our results provide valuable insights into the differences between subjective and quantitative assessments of morphological diversity.
-%**********************************
+
 \section{Conclusions}
@@
 However, our findings provide a foundation for future investigations and represent a significant step towards a more quantitative understanding of patterns of morphological and evolutionary diversity in tenrecs.
-%*******************************
-\section{Acknowledgements} %PeerJ have a separate section for funding acknowledgements
+
+\section{Acknowledgements}
 	We thank Thomas Guillerme, Fran\c{c}ois Gould and the members of NERD club for their insightful discussions and comments.
 Thank you to museum staff and curators for facilitating our access to their collections: Leona Leonard and Nigel Monaghan (Natural History Museum, Ireland), Roberto Portela Miguez and Paula Jenkins (Natural History Museum, London), Esther Langan (Smithsonian Institute NMNH), Eileen Westwig (American Museum of Natural History), Judy Chupasko (Museum of Comparative Zoology) and Bill Stanley and Steve Goodman (Field Museum).
-%********************************
+
+% Bibliography
+
 \bibliographystyle{sysbio} 

### 2015-01-28 paper/Diversity_MS.tex
Tried to fix formatting with new bst files but it's not working yet

@@
 % Title page
+
+% Title:
+
 \noindent
@@
 (MCZ) and Field Museum of Natural History, Chicago (FMNH).
-We used the taxonomy in Wilson and Reeder's Mammal Species of the World \citeyearpar{Wilson2005}, except for recently identified species where we used the taxonomy recorded on the specimen labels.
-Wilson and Reeder \citeyearpar{Wilson2005} record 30 species of tenrec but more recent studies indicate that there are now 34 species \citep[][]{Olson2013}.
-The additional species belong to the shrew tenrec (\textit{Microgale}) Genus and represent either recognition of cryptic species boundaries \citep{Olson2004} or discovery of new species \citep{Goodman2006, Olson2009}.
-Only one of these four recent additions, \textit{M.
-jobihely}, was present in the museum collections and therefore we could not include the three other newly recognised species in the analyses.
+We used the taxonomy in Wilson \& Reeder's Mammal Species of the World \citeyearpar{Wilson2005}, except for the recently discovered tenrec species \textit{Microgale jobihely}.
 We photographed all of the tenrec and golden mole skulls available in the collections.
-This included 31 of the 34 species in the tenrec Family and 12 of the 21 species of golden moles \citep{Wilson2005}.
+This included 31 of the 34 species in the tenrec Family \citep{Olson2013} and 12 of the 21 species of golden moles \citep{Wilson2005}.
 
 	We took pictures of the skulls using photographic copy stands.
-To take possible light variability into account, on each day we took a photograph of a white sheet of paper and used the custom white balance function on the camera to set the image as the baseline "white" measurement for those particular light conditions.
+To take possible light variability into account, we took a photograph of a white sheet of paper each day and used the custom white balance function on the camera to set the image as the baseline "white" measurement for those particular light conditions.
+We photographed the specimens with a Canon EOS 650D camera fitted with a EF 100 mm f/2.8 Macro USM lens and using a remote control (H\"ahnel Combi TF) to avoid camera shake.
+We photographed the specimens on a black material background with a light source in the top left-hand corner of the photograph.
+We used small bean bags to hold the specimens in position to ensure that they lay in a flat plane relative to the camera, and used the grid-line function on the live-view display screen of the camera to position the specimens in the centre of each image.
 
-	We photographed the specimens with a Canon EOS 650D camera fitted with a EF 100 mm f/2.8 Macro USM lens.
-We used a remote control (H\"ahnel Combi TF) to take the photos to avoid camera shake.
-We photographed the specimens on a black material background with a light source in the top left-hand corner of the photograph.
-We used small bean bags as necessary to hold the specimens in position while being photographed to ensure that they lay in a flat plane relative to the camera.
-We used the grid-line function on the live-view display screen of the camera to position the specimens in the centre of each image.
-
-	We photographed the skulls in three views: dorsal, ventral and lateral (right side) (Figure \ref{fig:flow}).
-When the right sides of the skulls were damaged or incomplete, we photographed the left sides and later reflected the images so that they could be compared to pictures of the right sides \citep[e.g.][]{Barrow2008}.
-
-	We converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}. 
-	Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute Natural History Museum are available on figshare in separate file sets for the dorsal \citep{Finlay2013d}, ventral \citep{Finlay2013v} and lateral \citep{Finlay2013l} skull views.
+	All skulls were photographed in three views: dorsal, ventral and lateral (right side) (Figure \ref{fig:flow}).
+When the right sides of the skulls were damaged or incomplete, we photographed the left sides and later reflected the images \citep[e.g.][]{Barrow2008}.
+After taking the photographs we converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}.
+Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute Natural History Museum are available on figshare (dorsal; \citet{Finlay2013d}, ventral; \citet{Finlay2013v} and lateral; \citet{Finlay2013l}).
 Copyright restrictions from the other museums prevent public sharing of their images but they are available on request.
 
-%-----------------------------------------
 \subsection{Geometric morphometric analyses}
@@
 We set the scale on each image individually to standardise for the different camera heights used when photographing the specimens.
-We created separate data files for each of the three morphometric analyses (skulls in dorsal, ventral and lateral views).
+We created separate data files for each of the three morphometric analyses (dorsal, ventral and lateral views).
 One of us (SF) digitised landmarks and semilandmark points on every image individually.
@@
 
-	Figure \ref{fig:landmarks} depicts that landmarks and curves which we used for each of the sets of photographs.
-For landmarks which are defined by dental structures, we used published dental sources \citep{Repenning1967, Eisenberg1969, Nowak1983, MacPhee1987, KnoxJones1992, Davis1997, Querouil2001, Nagorsen2002, Wilson2005, Goodman2006, Karatas2007, Hoffmann2008, Asher2008,  Muldoon2009, Lin2010} where available to identify the number and type of teeth in each species.
+	Figure \ref{fig:landmarks} depicts that landmarks and curves which we used for each skull view.
+For landmarks defined by dental structures, we used published dental sources \citep{Repenning1967, Eisenberg1969, Nowak1983, MacPhee1987, KnoxJones1992, Davis1997, Querouil2001, Nagorsen2002, Wilson2005, Goodman2006, Karatas2007, Hoffmann2008, Asher2008,  Muldoon2009, Lin2010} where available to identify the number and type of teeth in each species.
 Detailed descriptions of the landmarks can be found in the supplementary material.
-%****************************************************	
-	%Landmark pictures: 3 skulls together	
+
+% Landmark pictures: 3 skulls together	
 	\begin{figure}[!htbp]
@@
 
-%***************************************************
-
-%Maybe move this to the supplementary?
-% NC: Can it just be condensed?
 	When using semilandmark approaches there is a potential problem of over-sampling: simpler structures will require fewer semilandmarks to accurately represent their shape \citep{MacLeod2012}.
 To ensure that we applied a uniform standard of shape representation to each outline segment (i.e.
-that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012}.
-For each data set we chose a random selection of photos of specimens which represented the breadth of the morphological data (i.e.
-specimens from each sub-group of species).
-We drew the appropriate curves on each specimen and over-sampled the number of points on the curves.
-We measured the length of the line and regarded that as the 100\%, true length of that outline.
-We then re-sampled the curves with decreasing numbers of points and measured the length of the outlines.
-We calculated the length of each re-sampled curve as a percentage of the total length of the curve and then found the average percentage length for that reduced number of semilandmark points across all of the specimens in my test file.
-We continued this process until we found the minimum number of points that gave a curve length which was at least 95\% accurate.
-We repeated these curve-sampling tests for each analysis to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.
+that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012} to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.
 
@@
 We combined the landmarks and taxonomic identification files into a single morphometrics data object and carried out all further analyses in R version 3.1.1 \citep{Team2014}.
-Data and code for all of our analyses is available on GitHub \citep{Finlay2015c}.
 
-	At this stage, we either used the full data set (31 species of tenrec and 12 species of golden mole) or a reduced data set with just 17 species of tenrec (Figure \ref{fig:flow}).
-We created this reduced data set because the majority of tenrec species (19 out of 31 in our data) belong to the \textit{Microgale} (shrew-like) Genus that has relatively low morphological diversity \citep{Soarimalala2011, Jenkins2003}.
-This may mask signals of higher morphological diversity among other tenrecs.
-To test this, we created a subset of the tenrec data that included just five of the \textit{Microgale} species, each representing one of the five sub-divisions of \textit{Microgale} outlined by Soarimalala and Goodman \citeyearpar{Soarimalala2011}, i.e.
-small, small-medium, medium, large and long-tailed species.
-We compared the morphological diversity of this subset of tenrecs (n=17: five \textit{Microgale} and 12 non-\textit{Microgale} species) to that of the 12 species of golden moles (dashed arrows in Figure \ref{fig:flow}).
-After this selection stage, all further steps in the analyses were the same.
-
-	For each analysis, we used the \texttt{gpagen} function in the geomorph package \citep{Adams2013} to run a general Procrustes alignment \citep{Rohlf1993} of the landmark coordinates while sliding the semilandmarks by minimising Procrustes distance \citep{Bookstein1997}.
+	Next we used the \texttt{gpagen} function in the geomorph package \citep{Adams2013} to run a general Procrustes alignment \citep{Rohlf1993} of the landmark coordinates while sliding the semilandmarks by minimising Procrustes distance \citep{Bookstein1997}.
 We used these Procrustes-aligned coordinates of all specimens to calculate average shape values for each species which we then used for a principal components (PC) analysis with the \texttt{plotTangentSpace} function \citep{Adams2013}.
 We selected the number of principal component (PC) axes that accounted for 95\% of the variation in the data (Figure \ref{fig:flow}) and used these axes to estimate morphological diversity in each Family.
-%-------------------------------------------------------	
+
+ 	The majority of tenrec species (19 out of 31 in our data) belong to the \textit{Microgale} (shrew-like) Genus that has relatively low morphological diversity \citep{Soarimalala2011, Jenkins2003}.
+This may mask signals of higher morphological diversity among other tenrecs.
+To test this, we created a subset of the tenrec data that included just five of the \textit{Microgale} species, each representing one of the five sub-divisions of \textit{Microgale} outlined by Soarimalala \& Goodman \citeyearpar{Soarimalala2011}, i.e.
+small, small-medium, medium, large and long-tailed species.
+We repeated the general Procrustes alignment described above using this reduced data set.
+We then compared the morphological diversity of the full data set (31 species of tenrec) or a reduced data set with just 17 species of tenrec (five \textit{Microgale} and 12 non-\textit{Microgale} species; Figure \ref{fig:flow}) to that of the 12 species of golden moles.
+
 \subsection{Estimating morphological diversity}
@@
 
-%Diagram of mean distance to centroid (based on the diagram in Cooper et al 2009)
+% Diagram of mean distance to centroid
 	\begin{figure}[!htbp]
@@
 	\end{figure}
-%-------------------------------------------
+
 	One possible issue with these analyses is that the two Families have unequal sample sizes: 31 (or a subset of 17) tenrec species compared to just 12 golden mole species.
@@
 If this is true, when we randomly assign the group identity of each species (i.e.
-shuffle the "tenrec" and "golden mole" labels) and then re-compare the morphological diversity of the two groups, there would be no significant difference between these results and those obtained when the species are assigned to the correct groupings.
+shuffle the "tenrec" and "golden mole" labels) and then re-compare the morphological diversity of the two groups, there should be no significant difference between these results and those obtained when the species are assigned to the correct groupings.
+
 	We performed this shuffling procedure (random assignation of group identity) 1000 times and calculated the difference in morphological diversity between the two groups for each permutation.
@@
 This method automatically accounts for differences in sample size because shuffling of the group labels preserves the sample size of each group: there will always be 12 species labelled as "golden mole" and then, depending on the analysis, either 31 or 17 species labelled as "tenrec".
-Therefore, the 1000 permuted values of differences in morphological diversity create a distribution of the expected difference in diversity between a group of sample size 31 (or 17 in the case of the subsetted tenrec data) compared to a group of sample size 12 under the null hypothesis that the two groups have the same morphological diversity.
+Therefore, the 1000 permuted values of differences in morphological diversity create a distribution of the expected difference in diversity between a group of sample size 31 (or 17 in the case of the tenrec data subset) compared to a group of sample size 12 under the null hypothesis that the two groups have the same morphological diversity.
 We compared the observed measures of the differences in morphological diversity between the two Families to these null distributions to determine whether there were significant differences after taking sample size into account (two-tailed t test).
-%*********************************
-\section{Results} %PeerJ lists results and discussion together but I think it makes more sense to keep them separate
+Data and code for all of our analyses are available on GitHub \citep{Finlay2015c}.
+
+\section{Results} 
 	Figure \ref{fig:threePCA} depicts the morphospaces defined by the first two principal component (PC) axes from our principal components analyses (PCAs) of skull and mandible morphologies.
-The PCAs are based on the average Procrustes -superimposed shape coordinates for skulls in three views (dorsal, ventral and lateral).
-%-----------------------------
-%PCA figure with three plots
+The PCAs are based on the average Procrustes-superimposed shape coordinates for skulls in three views (dorsal, ventral and lateral).
+
 %PCA figure
-	%From the diversity_PCAplots_3panel
 	\begin{figure}[!htbp]
@@
 	\caption[Morphospace (principal components) plot of morphological diversity in tenrec and golden mole skulls.]
-		{Principal components plots of the morphospaces occupied by tenrecs (triangles, n=31 species) and golden moles (circles, n=12 species) for the skulls in dorsal (top left), ventral (top right) and lateral (bottom left) views.
+		{Principal components plots of the morphospaces occupied by tenrecs (triangles, n=31 species) and golden moles (circles, n=12 species) for skulls in dorsal (top left), ventral (top right) and lateral (bottom left) views.
 Each point represents the average skull shape of an individual species.
@@
 	\end{figure}
-%--------------------------
+
 	To compare morphological diversity in the two Families, we used the PC axes which accounted for 95\% of the cumulative variation in each of the skull analyses: dorsal (n=6 axes), ventral (n=7 axes) and lateral (n=7 axes).
 First, we compared the position of each Family within the morphospace plots.
-Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001 ), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72 , p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001 ) skull morphospaces,  indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure \ref{fig:threePCA}.
-
+Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72, p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001) skull morphospaces, indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure \ref{fig:threePCA}.
 	Second, we compared the morphological diversity within each Family.
@@
 In contrast, when we analysed morphological diversity of skulls within the sub-sample of 17 tenrecs (including just five \textit{Microgale} species) compared to the 12 golden mole species, we found that tenrec skulls were significantly more morphologically diverse than golden moles in all analyses (Table \ref{tab:diversity}).
+The pairwise permutation tests for each analysis confirmed that differences in morphological diversity were not artefacts of differences in sample size (Table \ref{tab:permutations})
 
-%----------------------------------------
-%Results table
-
+% Results table
 	\begin{table}[!htbp]			
@@
 
-%---------------------------------------------
-	The pairwise permutation tests for each analysis confirmed that differences in morphological diversity were not artefacts of differences in sample size (Table \ref{tab:permutations})
-%--------------------------------------------	
+% Permutations results table	
 \begin{table}[!htbp]			
@@
 	\end{table}
-%----------------------------------
+
 \section{Discussion}
-%Could move this paragraph to the conclusions
+
 	Tenrecs are often cited as an example of a mammalian group with high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}.
@@
 The different results for our analysis of lateral skull morphologies compared to dorsal and ventral views highlight the importance of using multiple approaches when studying 3D morphological shape using 2D geometric morphometrics techniques \citep{Arnqvist1998}.
-%I moved this paragraph up instead of leaving it in a separate caveats section	
+
     Landmark choice and placement will inevitably influence the results of a geometric morphometrics study.
@@
 	While there are clear physical differences among Family members \citep{Olson2013, Eisenberg1969}, the majority of tenrecs are very morphologically similar \citep{Jenkins2003} so morphological diversity in the Family as a whole is not as large as it first appears.
+
 	The goal of our study was to quantify morphological variation in tenrecs instead of relying on subjective assessments of their high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}.
@@
 Therefore future work should extend our approach beyond skulls to gain a more complete understanding of the overall morphological diversity of tenrecs and golden moles.
-	%I combined the paragraph above within the discussion (previously it was part of a separate caveats section)
 	While recognising these limitations, our results provide valuable insights into the differences between subjective and quantitative assessments of morphological diversity.
@@
 
-% Bibliography
+%********************************
 
-\bibliographystyle{sysbio} 
+%\bibliographystyle{systbio} 
+%I made my own bst style file but it doesn't fix the formatting issues
+	%I answered  yes for using an & instead of and in author lists and to have journal names in italics but it's not working
+\bibliographystyle{refstyle2}
+
 \bibliography{refs_paper}

### 2015-01-28 paper/Diversity_supplementary.tex

@@
 \usepackage{hyperref} %need this for url references
+\usepackage[parfill]{parskip}
 
-%\setcounter{secnumdepth}{0} % removes numbers from section headings
+\setcounter{secnumdepth}{0} % removes numbers from section headings
 \raggedright 			% justify the text on the left only
 \pagenumbering{arabic}
-\linespread{1.6}
+\linespread{1.3}
 
@@
 
-\title{
-       Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives.\\
-       \bigskip
-       Supplementary Material }
-\author{Sive Finlay and Natalie Cooper}
-\date{}
-\maketitle
-%I could take more out of the main paper and add it to here
-%---------------------------------------------------------
-%Landmarks 
-%---------------------------------------------------------
-\section{Landmark descriptions}
+{\centering\section{Supplementary Material}}
+
+\subsection{Landmark descriptions}
+\vspace*{-0.5cm}
 	The information below provides further details about the landmarks we used to summarise morphological shape in tenrec and golden mole skulls.
@@
 
-\subsection{Skulls: dorsal view}
+\subsubsection{Skulls: dorsal view}
+\vspace*{-0.5cm}
 	Most of our landmarks in this view are relative (type 3) points which represent overall morphological shape but not necessarily homologous biological features \citep{Zelditch2012}.
@@
 
-\subsection{Skulls: ventral view}
+\subsubsection{Skulls: ventral view}
+\vspace*{-0.5cm}
 	Most of the landmarks in this view are concentrated around the dentition and palate of the animals.
@@
 \newpage
-\subsection{Skulls: lateral view}
+\subsubsection{Skulls: lateral view}
+\vspace*{-0.5cm}
 	We placed nine landmarks on the photographs of skulls in lateral view and also drew two semilandmark curves to represent the shape of the back of the skull (between landmarks 7 and 8, re-sampled to 20 semilandmark points) and the top of the skull (between landmarks 8 and 1, re-sampled to 15 semilandmark points).
@@
 %-------------------------------------------
-\section{\normalfont{Potential morphometrics errors}}
-
+\subsection{{Potential morphometrics errors}}
+\vspace*{-0.5cm}	 
 	While 2D methods are an accepted means of comparing morphological shape \citep[e.g.][]{Adams2004, Mitteroecker2009}, particularly for comparing skull morphologies of small mammals \citep[e.g.][]{Cardini2003, Panchetti2008, White2008, Barrow2008, Scalici2011}, the inherent discrepancies associated with comparing three dimensional objects using two dimensional pictures can introduce some potential problems of possible image distortion \citep{Arnqvist1998}.
 Similarly, human error with how landmarks are positioned on specimens could also introduce noise into further analyses.
-
 	In contrast to detailed intraspecific work \citep[e.g.][]{Bornholdt2008, Blagojevic2011}, photographic or landmark placement errors are unlikely to be significant in our interspecific study since one would expect that the morphological variation among species is large enough to  be detected as a signal above any background noise associated with methodological error \citep{Arnqvist1998}.

### 2015-01-28 paper/Diversity_MS.tex
Separate submission folder, table labelling in supplementary
Fixed referencing
Added M jobihley reference

@@
 (MCZ) and Field Museum of Natural History, Chicago (FMNH).
-We used the taxonomy in Wilson \& Reeder's Mammal Species of the World \citeyearpar{Wilson2005}, except for the recently discovered tenrec species \textit{Microgale jobihely}.
+We used the taxonomy in Wilson \& Reeder's Mammal Species of the World \citeyearpar{Wilson2005}, except for the recently discovered tenrec species \textit{Microgale jobihely} \citep{Goodman2006}.
 We photographed all of the tenrec and golden mole skulls available in the collections.
@@
 
-	We used a combination of landmark and semilandmark analysis approaches to assess the shape variability in the skulls.
+	We used a combination of landmark and semilandmark approaches to assess the shape variability in the skulls.
 We used the TPS software suite \citep{Rohlf2013} to digitise landmarks and curves on the photos.
@@
 %********************************
-
-%\bibliographystyle{systbio} 
-%I made my own bst style file but it doesn't fix the formatting issues
-	%I answered  yes for using an & instead of and in author lists and to have journal names in italics but it's not working
-\bibliographystyle{refstyle2}
+%Custom bst file
+\bibliographystyle{refstyle}
 

### 2015-01-28 paper/Diversity_MS.tex
formatting changes

--- 2015-01-28 paper/Diversity_MS.tex
@@
 \usepackage{graphicx} 	
-\usepackage[nomarkers, nolists]{endfloat} 
+%\usepackage[nomarkers, nolists]{endfloat} 
 \usepackage{pdflscape}	
@@
 \usepackage{lineno} 
+\usepackage{ms}    	
 \usepackage{hyperref}
@@
 \pagenumbering{arabic}	
-\linenumbers
+%\linenumbers
 
-% Start of document
+% Title page information
+
+\title{Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives}
+
+\author{
+	Sive Finlay$^{1,2}$ and Natalie Cooper$^{1,2,*}$
+}
+
+\date{}
+
+\affiliation{\noindent{\footnotesize
+	$^1$ School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\ 
+	$^2$ Trinity Centre for Biodiversity Research, Trinity College Dublin, Dublin 2, Ireland.\\
+	$^*$Corresponding author: Natalie Cooper; ncooper@tcd.ie; Zoology Building, Trinity College Dublin, Dublin 2, Ireland. Tel: +353 1 896 1926.\\
+}}
+
+\vfill
+
+\runninghead{Morphological diversity in tenrecs}
+\keywords{disparity, golden moles, geometric morphometrics, morphology}
+
 \begin{document}
 
-\parindent=1.5em		
+\mstitlepage
+\parindent = 1.5em
 \addtolength{\parskip}{.3em}
-\doublespace
 
-% Title page
+\section{Abstract}
 
-% Title:
-
-\noindent
-\textsc{Sive Finlay$^{1,2}$ and Natalie Cooper$^{1,2,*}$}\\
-
-\noindent
-$^1$ School of Natural Sciences, Trinity College Dublin, Dublin 2, Ireland.\\ 
-\noindent
-$^2$ Trinity Centre for Biodiversity Research, Trinity College Dublin, Dublin 2, Ireland.\\
-\noindent
-$^*$Corresponding author: Natalie Cooper; ncooper@tcd.ie; Zoology Building, Trinity College Dublin, Dublin 2, Ireland. Tel: +353 1 896 1926.\\
-
-% Abstract
-
-	% Morphological diversity is often studied qualitatively.
+	Morphological diversity is often studied qualitatively.
 However, to truly understand the evolution of exceptional diversity, it is important to take a quantitative approach instead of relying on subjective, qualitative assessments.
@@
 
-	% Tenrecs are often cited as an example of an exceptionally morphologically diverse group.
+	Tenrecs are often cited as an example of an exceptionally morphologically diverse group.
 However, this assumption has not been tested quantitatively.
@@
 
-	% Contrary to our expectations, We find that tenrec skulls are only more morphologically diverse than golden moles when measured in lateral view.
+	Contrary to our expectations, We find that tenrec skulls are only more morphologically diverse than golden moles when measured in lateral view.
 Furthermore, similarities among the species-rich \textit{Microgale} tenrec Genus appear to mask higher morphological diversity in the rest of the Family.
@@
 \newpage
+\raggedright
+\doublespacing
+\setlength{\parindent}{1cm}
+
 \section{Introduction}
@@
 Thank you to museum staff and curators for facilitating our access to their collections: Leona Leonard and Nigel Monaghan (Natural History Museum, Ireland), Roberto Portela Miguez and Paula Jenkins (Natural History Museum, London), Esther Langan (Smithsonian Institute NMNH), Eileen Westwig (American Museum of Natural History), Judy Chupasko (Museum of Comparative Zoology) and Bill Stanley and Steve Goodman (Field Museum).
+This work was funded by an Irish Research Council EMBARK Initiative Postgraduate Scholarship (SF) and a European Commission CORDIS Seventh Framework Programme (FP7) Marie Curie CIG grant (proposal number: 321696; NC).
 
-%********************************
-
-%\bibliographystyle{systbio} 
-%I made my own bst style file but it doesn't fix the formatting issues
-	%I answered  yes for using an & instead of and in author lists and to have journal names in italics but it's not working
-\bibliographystyle{refstyle2}
-
+\bibliographystyle{sysbio} 
 \bibliography{refs_paper}

### 2015-01-28 paper/PeerJ_submission/Manuscript.tex

--- 2015-01-28 paper/Diversity_MS.tex
@@
 
-% Title:
+% Title: Morphological diversity in tenrecs (Afrosoricida, Tenrecidae): Comparing tenrec skull diversity to their closest relatives
 
@@
 	Our methods involved i) data collection, ii) geometric morphometric analyses and iii) estimating morphological diversity.
-For clarity,  Figure \ref{fig:flow} summarises all of these steps and we describe them in detail below.
-
-% Methods flow chart
-	\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=1\linewidth,height=0.8\textheight]{figures/methods_flowchart_paper.png}
-
-	\caption[Flowchart diagram of data collection and analysis]
-		{Summary of the main steps in our data collection, processing and analysis protocol.
-Note that the analyses were repeated separately for each set of photographs: skulls in dorsal, ventral and lateral views.
-The dashed arrows refer to the stage at which we selected a subsample of the tenrecs (including just five species of the \textit{Microgale} Genus) so that we could compare the morphological diversity of this reduced subsample of tenrec species to the diversity of golden moles.}
-		\label{fig:flow}
-		\end{figure}
+For clarity,  Figure 1 summarises all of these steps and we describe them in detail below.
 
@@
 
-	All skulls were photographed in three views: dorsal, ventral and lateral (right side) (Figure \ref{fig:flow}).
+	All skulls were photographed in three views: dorsal, ventral and lateral (right side) (Figure 1).
 When the right sides of the skulls were damaged or incomplete, we photographed the left sides and later reflected the images \citep[e.g.][]{Barrow2008}.
@@
 
-	Figure \ref{fig:landmarks} depicts that landmarks and curves which we used for each skull view.
+	Figure 2 depicts that landmarks and curves which we used for each skull view.
 For landmarks defined by dental structures, we used published dental sources \citep{Repenning1967, Eisenberg1969, Nowak1983, MacPhee1987, KnoxJones1992, Davis1997, Querouil2001, Nagorsen2002, Wilson2005, Goodman2006, Karatas2007, Hoffmann2008, Asher2008,  Muldoon2009, Lin2010} where available to identify the number and type of teeth in each species.
 Detailed descriptions of the landmarks can be found in the supplementary material.
-
-% Landmark pictures: 3 skulls together	
-	\begin{figure}[!htbp]
-		\centering
-		\includegraphics[width=1\linewidth]{figures/skdors+skvent+sklat_BW.png}
-		\caption[Skulls: dorsal, ventral and lateral landmarks]
-		{Landmarks (numbered points) and curves (outlines) for the skulls in dorsal,ventral and lateral view.
-See the supplementary material for detailed landmark descriptions.
-The skulls are two different specimens of \textit{Potamogale velox} (otter shrew tenrec), museum accession numbers AMNH 51327 (dorsal picture) and BMNH 1934.6.16.2 (ventral and lateral pictures).
-}
-		\label{fig:landmarks}
-	\end{figure}
 
@@
 We used these Procrustes-aligned coordinates of all specimens to calculate average shape values for each species which we then used for a principal components (PC) analysis with the \texttt{plotTangentSpace} function \citep{Adams2013}.
-We selected the number of principal component (PC) axes that accounted for 95\% of the variation in the data (Figure \ref{fig:flow}) and used these axes to estimate morphological diversity in each Family.
+We selected the number of principal component (PC) axes that accounted for 95\% of the variation in the data (Figure 1) and used these axes to estimate morphological diversity in each Family.
 
@@
 We repeated the general Procrustes alignment described above using this reduced data set.
-We then compared the morphological diversity of the full data set (31 species of tenrec) or a reduced data set with just 17 species of tenrec (five \textit{Microgale} and 12 non-\textit{Microgale} species; Figure \ref{fig:flow}) to that of the 12 species of golden moles.
+We then compared the morphological diversity of the full data set (31 species of tenrec) or a reduced data set with just 17 species of tenrec (five \textit{Microgale} and 12 non-\textit{Microgale} species; Figure 1) to that of the 12 species of golden moles.
 
@@
 
-	We grouped the PC scores for tenrecs and golden moles separately so that we could estimate the diversity of each Family and then compare the two groups (Figure \ref{fig:flow}).
+	We grouped the PC scores for tenrecs and golden moles separately so that we could estimate the diversity of each Family and then compare the two groups (Figure 1).
 We compared morphological diversity in two ways.
@@
 Second, we compared morphological diversity within tenrecs to the diversity within golden moles.
-We define morphological diversity as the mean Euclidean distance (sum of squared differences) between each species and its Family centroid (Figure \ref{fig:centroids}).
+We define morphological diversity as the mean Euclidean distance (sum of squared differences) between each species and its Family centroid (Figure 3).
 This is summarised in the equation below where \textit{n} is the number of species in the Family, \textit{i} is the number of PC axes and \textit{c} is the average PC score for each axis (the centroid).
@@
 	If tenrecs are more morphologically diverse than golden moles, then they should be more dispersed within the morphospaces and have, on average, higher values of mean Euclidean distance.
-
-% Diagram of mean distance to centroid
-	\begin{figure}[!htbp]
-	\centering
-	\includegraphics [width=0.7\linewidth, height=0.7\textheight, keepaspectratio]{figures/Centroids.png}
-	\caption[Calculating diversity as mean Euclidean distance to Family centroid.]
-		{Estimating morphological diversity as the mean Euclidean distance between each species and the Family centroid.
-Every species had scores on the principal components (PC) axes that accounted for 95\% of the variation in the principal components analysis.
-The number of axes (PCn) varied for each analysis but they were the same within a single analysis.
-PC scores were used to calculate the Euclidean distance from each species to the Family centroid (average (\begin{math}
-			\bar{x}
-			\end{math}) PC scores for the entire Family). Morphological diversity of the Family is the average value of these Euclidean distances.}
-	\label{fig:centroids}
-	\end{figure}
 
@@
 \section{Results} 
-	Figure \ref{fig:threePCA} depicts the morphospaces defined by the first two principal component (PC) axes from our principal components analyses (PCAs) of skull and mandible morphologies.
+	Figure 4 depicts the morphospaces defined by the first two principal component (PC) axes from our principal components analyses (PCAs) of skull and mandible morphologies.
 The PCAs are based on the average Procrustes-superimposed shape coordinates for skulls in three views (dorsal, ventral and lateral).
-
-%PCA figure
-	\begin{figure}[!htbp]
-	\centering
-	\includegraphics[width=1\linewidth, height=1\textheight, keepaspectratio]{figures/PCA_threeplot.png}
-	\caption[Morphospace (principal components) plot of morphological diversity in tenrec and golden mole skulls.]
-		{Principal components plots of the morphospaces occupied by tenrecs (triangles, n=31 species) and golden moles (circles, n=12 species) for skulls in dorsal (top left), ventral (top right) and lateral (bottom left) views.
-Each point represents the average skull shape of an individual species.
-Axes are principal component 1 (PC1) and principal component 2 (PC2) of the average scores from principal components analyses of mean Procrustes shape coordinates for each species.}
-	\label{fig:threePCA}
-	\end{figure}
 
@@
 First, we compared the position of each Family within the morphospace plots.
-Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72, p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001) skull morphospaces, indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure \ref{fig:threePCA}.
+Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72, p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001) skull morphospaces, indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure 4).
 	Second, we compared the morphological diversity within each Family.
-Based on our measures of mean Euclidean distance to the Family centroids, tenrec skulls are more morphologically diverse than golden mole skulls when they are measured in lateral view but not in dorsal or ventral view (Table \ref{tab:diversity}).
-In contrast, when we analysed morphological diversity of skulls within the sub-sample of 17 tenrecs (including just five \textit{Microgale} species) compared to the 12 golden mole species, we found that tenrec skulls were significantly more morphologically diverse than golden moles in all analyses (Table \ref{tab:diversity}).
-The pairwise permutation tests for each analysis confirmed that differences in morphological diversity were not artefacts of differences in sample size (Table \ref{tab:permutations})
-
-% Results table
-	\begin{table}[!htbp]			
-		\caption[Comparing morphological diversity in tenrecs and golden moles.]
-		{Morphological diversity in tenrecs compared to golden moles (12 species).
-N is the number of tenrec species: 31 species or 17 species including just five representatives of the \textit{Microgale} Genus.
-Morphological diversity of the Family is the mean Euclidean distance from each species to the Family centroid.
-Significant differences between the two Families (p$<$0.05) from two-tailed t-tests are highlighted in bold.}
-		\input{tables/diversity.results} 
-		\label{tab:diversity}  
-	\end{table}
-
-% Permutations results table	
-\begin{table}[!htbp]			
-	\caption[Results of the permutation tests]{Results of the permutation analyses comparing the observed differences in morphological diversity to a null distribution of expected results.
-Morphological diversity of the Family is the mean Euclidean distance from each species to the Family centroid.
-Results are shown for both the full (N=31 species of tenrec compared to 12 species of golden mole) and reduced (N=17 species of tenrec compared to 12 golden moles) data sets.
-Significant values (p$<$0.05) indicate that the observed morphological diversity is different to the expected differences under a null hypothesis of equivalent diversities in the two Families.}
-		\input{tables/perm.results} 
-		\label{tab:permutations}  
-	\end{table}
+Based on our measures of mean Euclidean distance to the Family centroids, tenrec skulls are more morphologically diverse than golden mole skulls when they are measured in lateral view but not in dorsal or ventral view (Table 1).
+In contrast, when we analysed morphological diversity of skulls within the sub-sample of 17 tenrecs (including just five \textit{Microgale} species) compared to the 12 golden mole species, we found that tenrec skulls were significantly more morphologically diverse than golden moles in all analyses (Table 1).
+The pairwise permutation tests for each analysis confirmed that differences in morphological diversity were not artefacts of differences in sample size (Table 2)
 
@@
 
-	In our full analysis, tenrecs only had higher morphological diversity than golden moles when the skulls were measured in lateral view (Table \ref{tab:diversity}).
+	In our full analysis, tenrecs only had higher morphological diversity than golden moles when the skulls were measured in lateral view (Table 1).
 There was no difference in morphological diversity when we analysed the skulls in dorsal or ventral views.
 This is most likely due to our choice of landmarks.
-The two outline curves in lateral view (Figure \ref{fig:landmarks}) emphasise morphological variation in the back and top of the skulls.
+The two outline curves in lateral view (Figure 2) emphasise morphological variation in the back and top of the skulls.
 These curves summarise overall shape variation but they do not identify clear anatomical differences because they are defined by relative features rather than homologous structures \citep{Zelditch2012}.
@@
 	These lateral aspects of the skull morphology were not visible in the dorsal and ventral photographs so they could not be included in those analyses.
-In contrast, our landmarks in the dorsal, and particularly ventral, views focus on morphological variation in the overall outline shape of the sides of the skull and palate (Figure \ref{fig:landmarks}).
+In contrast, our landmarks in the dorsal, and particularly ventral, views focus on morphological variation in the overall outline shape of the sides of the skull and palate (Figure 2).
 The result that tenrecs are no more diverse than golden moles in these areas makes intuitive sense: most tenrecs have broad, non-specialised diets \citep{Olson2013} so there is no obvious functional reason why they should have particularly diverse palate morphologies.
@@
 If a particular morphotype is over-represented then the similarities among those species will reduce the overall morphological variation within the group \citep{Foote1991}.
-This appears to be the case for our data; it was only when we included a sub-sample of \textit{Microgale} tenrecs that we found higher morphological diversity in tenrecs compared to golden moles across all three skull analyses (Table \ref{tab:diversity}).
+This appears to be the case for our data; it was only when we included a sub-sample of \textit{Microgale} tenrecs that we found higher morphological diversity in tenrecs compared to golden moles across all three skull analyses (Table 1).
 	While there are clear physical differences among Family members \citep{Olson2013, Eisenberg1969}, the majority of tenrecs are very morphologically similar \citep{Jenkins2003} so morphological diversity in the Family as a whole is not as large as it first appears.
@@
 
-%********************************
+% Bibliography
 
-%\bibliographystyle{systbio} 
-%I made my own bst style file but it doesn't fix the formatting issues
-	%I answered  yes for using an & instead of and in author lists and to have journal names in italics but it's not working
-\bibliographystyle{refstyle2}
-
+\bibliographystyle{sysbio} 
 \bibliography{refs_paper}
@@
 \end{document}
+
+% Figure and Table legends
+
+% Figure 1: Flowchart diagram of data collection and analysis
+% Summary of the main steps in our data collection, processing and analysis protocol.
+Note that the analyses were repeated separately for each set of photographs: skulls in dorsal, ventral and lateral views.
+The dashed arrows refer to the stage at which we selected a subsample of the tenrecs (including just five species of the \textit{Microgale} Genus) so that we could compare the morphological diversity of this reduced subsample of tenrec species to the diversity of golden moles.
+
+% Figure 2: Skulls: dorsal, ventral and lateral landmarks
+% Landmarks (numbered points) and curves (outlines) for the skulls in dorsal,ventral and lateral view.
+See the supplementary material for detailed landmark descriptions.
+The skulls are two different specimens of \textit{Potamogale velox} (otter shrew tenrec), museum accession numbers AMNH 51327 (dorsal picture) and BMNH 1934.6.16.2 (ventral and lateral pictures).
+
+% Figure 3: Calculating diversity as mean Euclidean distance to Family centroid.
+% Estimating morphological diversity as the mean Euclidean distance between each species and the Family centroid.
+Every species had scores on the principal components (PC) axes that accounted for 95\% of the variation in the principal components analysis.
+The number of axes (PCn) varied for each analysis but they were the same within a single analysis.
+PC scores were used to calculate the Euclidean distance from each species to the Family centroid (average PC scores for the entire Family).
+Morphological diversity of the Family is the average value of these Euclidean distances.
+
+% Figure 4: Morphospace (principal components) plot of morphological diversity in tenrec and golden mole skulls
+% Principal components plots of the morphospaces occupied by tenrecs (triangles, n=31 species) and golden moles (circles, n=12 species) for skulls in dorsal (top left), ventral (top right) and lateral (bottom left) views.
+Each point represents the average skull shape of an individual species.
+Axes are principal component 1 (PC1) and principal component 2 (PC2) of the average scores from principal components analyses of mean Procrustes shape coordinates for each species.
+
+% Table 1: Comparing morphological diversity in tenrecs and golden moles.
+% Morphological diversity in tenrecs compared to golden moles (12 species).
+N is the number of tenrec species: 31 species or 17 species including just five representatives of the \textit{Microgale} Genus.
+Morphological diversity of the Family is the mean Euclidean distance from each species to the Family centroid.
+Significant differences between the two Families (p$<$0.05) from two-tailed t-tests are highlighted in bold.
+
+% Table 2: Results of the permutation tests
+% Results of the permutation analyses comparing the observed differences in morphological diversity to a null distribution of expected results.
+Morphological diversity of the Family is the mean Euclidean distance from each species to the Family centroid.
+Results are shown for both the full (N=31 species of tenrec compared to 12 species of golden mole) and reduced (N=17 species of tenrec compared to 12 golden moles) data sets.
+Significant values (p$<$0.05) indicate that the observed morphological diversity is different to the expected differences under a null hypothesis of equivalent diversities in the two Families.

### 2015-01-28 paper/Supplemental.tex
Supplemental for PeerJ submission

--- 2015-01-28 paper/Diversity_supplementary.tex
@@
 
+%Label tables as S1, S2 etc.	
+\newcommand{\beginsupplement}{%
+	       \setcounter{table}{0}
+	        \renewcommand{\thetable}{S\arabic{table}}%
+	        \setcounter{figure}{0}
+	        \renewcommand{\thefigure}{S\arabic{figure}}%
+	     }
+
 \begin{document}
+\beginsupplement
 
@@
 We placed ten landmarks and drew four semilandmark curves to represent the shape of both the braincase (posterior) and nasal (anterior) area of the skulls.
-Table \ref{tab:skdors} describes how we defined the landmarks and outline curves for our images of skulls in dorsal view.
-
-%Table with skdors landmark descriptions
-\begin{table}[h]
-	\caption[Skulls: dorsal landmarks]
-		{Descriptions of the landmarks (points) and curves (semilandmarks) for the skulls in dorsal view} 
-	\input{tables/skdors.landmarks}
-	\label{tab:skdors}
-\end{table}
+Table S1 describes how we defined the landmarks and outline curves for our images of skulls in dorsal view.
 %--------------------------------------------------------------
@@
 The high variability of our species' basi-cranial regions and difficulties associated with identifying developmentally or functionally homologous points precluded designation of additional landmarks towards the back of the skulls.
-Table \ref{tab:skvent} outlines the descriptions of the landmarks we used for the ventral skull photos.
-
-% Skulls ventral landmarks
-\begin{table}[!htb] 
-\caption[Skulls: ventral landmarks]
-		{Descriptions of the landmarks (points) and curves (semilandmarks) for the skulls in ventral view.} 
-\input{tables/skvent.landmarks}
-\label{tab:skvent}
-\\
-*This curve does not necessarily trace homologous features because of the variation in the position of the foramen magnum.
-\end{table}
+Table S2 outlines the descriptions of the landmarks we used for the ventral skull photos.
 
@@
 	We placed nine landmarks on the photographs of skulls in lateral view and also drew two semilandmark curves to represent the shape of the back of the skull (between landmarks 7 and 8, re-sampled to 20 semilandmark points) and the top of the skull (between landmarks 8 and 1, re-sampled to 15 semilandmark points).
-Table \ref{tab:sklat} describes our definitions for each of the landmark points.
+Table S3 describes our definitions for each of the landmark points.
 	If specimens were damaged on their right side we reflected photographs of the left lateral side of the skull so that all the images were in the same orientation.
 
-% Skulls lateral landmarks
-\begin{table}[!htb]
-\caption[Skulls: lateral landmarks]
-		{Descriptions of the landmarks (points) and curves (semilandmarks) for the skulls in lateral view.} 
-\input{tables/sklat.landmarks}
-\label{tab:sklat}
-\end{table}
 %-------------------------------------------
@@
 \end{document}
+
+%--------------------------------------------
+%Table legends
+%Table S1 Skulls: dorsal landmarks
+%Descriptions of the landmarks (points) and curves (semilandmarks) for the skulls in dorsal view.
+
+% Table S2 Skulls: ventral landmarks
+%Descriptions of the landmarks (points) and curves (semilandmarks) for the skulls in ventral view.
+
+% Table S3 Skulls: lateral landmarks
+%Descriptions of the landmarks (points) and curves (semilandmarks) for the skulls in lateral view.

### 2015-03-12 paper/Manuscript.tex
Last edits before submission: fixed the diversity equation
Responses to editor's comments

--- 2015-01-28 paper/PeerJ_submission/Manuscript.tex
@@
 However, to truly understand the evolution of exceptional diversity, it is important to take a quantitative approach instead of relying on subjective, qualitative assessments.
-Here, we present a quantitative analysis of morphological diversity in a Family of small mammals, the tenrecs (Afrosoricida, Tenrecidae).
+Here, we present a quantitative analysis of morphological diversity in a family of small mammals, the tenrecs (Afrosoricida, Tenrecidae).
 
@@
 	% Contrary to our expectations, We find that tenrec skulls are only more morphologically diverse than golden moles when measured in lateral view.
-Furthermore, similarities among the species-rich \textit{Microgale} tenrec Genus appear to mask higher morphological diversity in the rest of the Family.
+Furthermore, similarities among the species-rich \textit{Microgale} tenrec genus appear to mask higher morphological diversity in the rest of the family.
 These results reveal new insights into the morphological diversity of tenrecs and highlight the importance of using quantitative methods to test qualitative assumptions about patterns of morphological diversity.
@@
 
-	Analysing patterns of morphological diversity has important implications for our understanding of ecological and evolutionary traits.
-Species morphology can influence niche occupancy and affect speciation and diversification rates through time \citep{Price2012}.
-High morphological diversity is also a unifying \citep{Losos2010a, Olson2009}, although not defining \citep{Glor2010, Olson2009}, characteristic of adaptive radiations.
-Furthermore, analysing morphological convergences in groups such as freshwater cichlid fish \citep{Muschick2012} and anole lizards \citep{Mahler2013} provides insights into the relative repeatability of evolution \citep{Losos2011}.
+	Analysing patterns of morphological diversity (the variation in physical form \citep{Foote1997} has important implications for our understanding of ecological and evolutionary traits.
+Increasingly, many studies recognise the importance of quantifying the degree of morphological diversity instead of relying on subjective assessments of diversity in form \citep[e.g.][]{Ruta2013,Hopkins2013, Goswami2011,Drake2010, Price2010, Brusatte2008}.
+We need to quantify the morphological similarities and differences among species to gain a better understanding of their ecological interactions and evolutionary history.
 
-	Although studies of morphological diversity have clear implications for our understanding of ecological and evolutionary patterns, apart from a few examples \citep[e.g.][]{Ruta2013, Goswami2011, Brusatte2008}, it is still common to study morphological diversity from a qualitative rather than quantitative perspective.
-However, we need to quantify the morphological similarities and differences among species to gain a better understanding of their ecological interactions and evolutionary history.
 	Unfortunately, morphological diversity is difficult to quantify.
-Studies are inevitably constrained to measure the diversity of specific traits rather than overall morphologies \citep{Roy1997}.
+Many studies are constrained to measuring the diversity of specific traits rather than overall morphologies \citep{Roy1997}.
 In addition, our perception of morphological diversity is influenced by the trait being used, and results may depend on the particular trait being analysed \citep{Foth2012}.
@@
 This method captures more of the true, overall anatomical shape of particular structures \citep{Mitteroecker2009}.
+In particular, two-dimensional geometric morphometric approaches are commonly used to analyse 3D morphological shape and are appropriate for cross-species comparisons \citep[e.g.][]{Muschick2012, Panchetti2008, Wroe2007}.
+Any bias from 2D representation of a 3D structure is unlikely to be a significant issue for interspecific studies as the overall shape variation among species is geater than discrepancies introduced by using 2D morphometric techniques \citep{Cardinin2014}.
 These more detailed approaches are useful tools for studying patterns of morphological diversity.
 
-	Here we apply geometric morphometric techniques to quantify morphological diversity in a Family of small mammals, the tenrecs.
-Tenrecs (Afrosoricida, Tenrecidae) are a morphologically diverse group that is commonly cited as an example of both convergent evolution and an adaptive radiation \citep{Soarimalala2011, Eisenberg1969}.
-The Family is comprised of 34 species, 31 of which are endemic to Madagascar \citep{Olson2013}.
+	Here we apply geometric morphometric techniques to quantify morphological diversity in a family of small mammals, the tenrecs.
+Tenrecs (Afrosoricida, Tenrecidae) are a morphologically diverse group that researchers often identify as an example of both convergent evolution and an adaptive radiation \citep{Soarimalala2011, Eisenberg1969}.
+The family is comprised of 34 species, 31 of which are endemic to Madagascar \citep{Olson2013}.
 Body masses of tenrecs span three orders of magnitude (2.5 to $>$ 2,000g); a greater range than all other Families, and most Orders, of living mammals \citep{Olson2003}.
@@
 	We expect tenrecs to be more morphologically diverse than golden moles because tenrecs occupy a wider variety of ecological niches.
-The tenrec Family includes terrestrial, semi-fossorial, semi-aquatic and semi-arboreal species \citep{Soarimalala2011}.
+The tenrec family includes terrestrial, semi-fossorial, semi-aquatic and semi-arboreal species \citep{Soarimalala2011}.
 In contrast, all golden moles occupy very similar, fossorial ecological niches \citep{Bronner1995}.
@@
 We photographed all of the tenrec and golden mole skulls available in the collections.
-This included 31 of the 34 species in the tenrec Family \citep{Olson2013} and 12 of the 21 species of golden moles \citep{Wilson2005}.
+This included 31 of the 34 species in the tenrec family \citep{Olson2013} and 12 of the 21 species of golden moles \citep{Wilson2005}.
 
@@
 When the right sides of the skulls were damaged or incomplete, we photographed the left sides and later reflected the images \citep[e.g.][]{Barrow2008}.
+Some specimens were too damaged to use in particular views so there were a different total number of images for each analysis.
+Our final data sets included photographs of 182 skulls in dorsal view (148 tenrecs and 34 golden moles), 173 skulls in ventral view (141 tenrecs and 32 golden moles) and 171 skulls in lateral view (140 tenrecs and 31 golden moles).
 After taking the photographs we converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}.
@@
 One of us (SF) digitised landmarks and semilandmark points on every image individually.
-Some specimens were too damaged to use in particular views so there were a different total number of images for each analysis.
-Our final data sets included photographs of 182 skulls in dorsal view (148 tenrecs and 34 golden moles), 173 skulls in ventral view (141 tenrecs and 32 golden moles) and 171 skulls in lateral view (140 tenrecs and 31 golden moles).
 
-	Figure 2 depicts that landmarks and curves which we used for each skull view.
-For landmarks defined by dental structures, we used published dental sources \citep{Repenning1967, Eisenberg1969, Nowak1983, MacPhee1987, KnoxJones1992, Davis1997, Querouil2001, Nagorsen2002, Wilson2005, Goodman2006, Karatas2007, Hoffmann2008, Asher2008,  Muldoon2009, Lin2010} where available to identify the number and type of teeth in each species.
+	Figure 2 depicts the landmarks and curves which we used for each skull view.
+For landmarks defined by dental structures, we used published dental sources where available \citep{Repenning1967, Eisenberg1969, Nowak1983, MacPhee1987, KnoxJones1992, Davis1997, Querouil2001, Nagorsen2002, Wilson2005, Goodman2006, Karatas2007, Hoffmann2008, Asher2008,  Muldoon2009, Lin2010}  to identify the number and type of teeth in each species.
 Detailed descriptions of the landmarks can be found in the supplementary material.
@@
 
-	Next we used the \texttt{gpagen} function in the geomorph package \citep{Adams2013} to run a general Procrustes alignment \citep{Rohlf1993} of the landmark coordinates while sliding the semilandmarks by minimising Procrustes distance \citep{Bookstein1997}.
+	Next we used the \texttt{gpagen} function in version 2.1 of the geomorph package \citep{Adams2014a, Adams2013} to run a general Procrustes alignment \citep{Rohlf1993} of the landmark coordinates while sliding the semilandmarks by minimising Procrustes distance \citep{Bookstein1997}.
 We used these Procrustes-aligned coordinates of all specimens to calculate average shape values for each species which we then used for a principal components (PC) analysis with the \texttt{plotTangentSpace} function \citep{Adams2013}.
-We selected the number of principal component (PC) axes that accounted for 95\% of the variation in the data (Figure 1) and used these axes to estimate morphological diversity in each Family.
+We selected the number of principal component (PC) axes that accounted for 95\% of the variation in the data (Figure 1) and used these axes to estimate morphological diversity in each family.
 
- 	The majority of tenrec species (19 out of 31 in our data) belong to the \textit{Microgale} (shrew-like) Genus that has relatively low morphological diversity \citep{Soarimalala2011, Jenkins2003}.
+ 	The majority of tenrec species (19 out of 31 in our data) belong to the \textit{Microgale} (shrew-like) genus that has relatively low morphological diversity \citep{Soarimalala2011, Jenkins2003}.
 This may mask signals of higher morphological diversity among other tenrecs.
@@
 
-	We grouped the PC scores for tenrecs and golden moles separately so that we could estimate the diversity of each Family and then compare the two groups (Figure 1).
+	We grouped the PC scores for tenrecs and golden moles separately so that we could estimate the diversity of each family and then compare the two groups (Figure 1).
 We compared morphological diversity in two ways.
@@
 Second, we compared morphological diversity within tenrecs to the diversity within golden moles.
-We define morphological diversity as the mean Euclidean distance (sum of squared differences) between each species and its Family centroid (Figure 3).
-This is summarised in the equation below where \textit{n} is the number of species in the Family, \textit{i} is the number of PC axes and \textit{c} is the average PC score for each axis (the centroid).
+We define morphological diversity as the mean Euclidean distance (sum of squared differences) between each species and its family centroid (Figure 3).
+This is summarised in the equation below where \textit{n} is the number of species in the family, \textit{i} is the number of PC axes and \textit{c} is the average PC score for each axis (the centroid).
 
 	\begin{equation}
-		Disparity = \frac{\sqrt{\Sigma(PCn_{i}-PCc_{i})^2}}{n}
+		Diversity = \frac{\sqrt{\Sigma(PCn_{i}-PCc_{i})^2}}{n}
 	\end{equation}
@@
 Morphological diversity is usually decoupled from taxonomic diversity \citep[e.g.][]{Ruta2013, Hopkins2013} so larger groups are not necessarily more morphologically diverse.
-However, comparing morphological diversity in tenrecs to the diversity of a smaller Family could still bias the results.
+However, comparing morphological diversity in tenrecs to the diversity of a smaller family could still bias the results.
 We used pairwise permutation tests to account for this potential issue.
 
-	We tested the null hypothesis that tenrecs and golden moles have the same morphological diversity (the same mean Euclidean distance to the Family centroid).
+	We tested the null hypothesis that tenrecs and golden moles have the same morphological diversity (the same mean Euclidean distance to the family centroid).
 If this is true, when we randomly assign the group identity of each species (i.e.
@@
 	To compare morphological diversity in the two Families, we used the PC axes which accounted for 95\% of the cumulative variation in each of the skull analyses: dorsal (n=6 axes), ventral (n=7 axes) and lateral (n=7 axes).
-First, we compared the position of each Family within the morphospace plots.
+First, we compared the position of each family within the morphospace plots.
 Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72, p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001) skull morphospaces, indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure 4).
-	Second, we compared the morphological diversity within each Family.
-Based on our measures of mean Euclidean distance to the Family centroids, tenrec skulls are more morphologically diverse than golden mole skulls when they are measured in lateral view but not in dorsal or ventral view (Table 1).
+	Second, we compared the morphological diversity within each family.
+Based on our measures of mean Euclidean distance to the family centroids, tenrec skulls are more morphologically diverse than golden mole skulls when they are measured in lateral view but not in dorsal or ventral view (Table 1).
 In contrast, when we analysed morphological diversity of skulls within the sub-sample of 17 tenrecs (including just five \textit{Microgale} species) compared to the 12 golden mole species, we found that tenrec skulls were significantly more morphologically diverse than golden moles in all analyses (Table 1).
@@
 The different results for our analysis of lateral skull morphologies compared to dorsal and ventral views highlight the importance of using multiple approaches when studying 3D morphological shape using 2D geometric morphometrics techniques \citep{Arnqvist1998}.
+Future analyses could use 3D geometric morphometric approaches to test whether similar patterns emerge.
 
     Landmark choice and placement will inevitably influence the results of a geometric morphometrics study.
-Our interest in broad-scale, cross-taxonomic comparisons of cranial morphology constrained our choice of landmarks to those that could be accurately identified in many different species \citep[e.g.][]{Ruta2013, Goswami2011, Wroe2007}.
-In contrast, studies that use skulls to characterise morphological variation within species \citep[e.g.][]{Blagojevic2011, Bornholdt2008} or to delineate species boundaries within a clade \citep[e.g.][]{Panchetti2008} tend to focus on more detailed, biologically homologous landmarks \citep{Zelditch2012}.
+Our interest in broad-scale, cross-taxonomic comparisons of cranial morphology constrained our choice of landmarks to those that could be accurately identified in many different species \citep[e.g.][]{Ruta2013, Goswami2011, Wroe2007, Goswami2006}.
+In contrast, studies that use skulls to characterise morphological variation within species \citep[e.g.][]{Blagojevic2011, Giannini2010, Flores2010, Bornholdt2008} or to delineate species boundaries within a clade \citep[e.g.][]{Panchetti2008} tend to focus on more detailed, biologically homologous landmarks \citep{Zelditch2012}.
 Repeating our analyses with a narrower taxonomic focus may give greater insight into the specific morphological differences among subgroups of tenrecs and golden moles.
@@
 This appears to be the case for our data; it was only when we included a sub-sample of \textit{Microgale} tenrecs that we found higher morphological diversity in tenrecs compared to golden moles across all three skull analyses (Table 1).
-	While there are clear physical differences among Family members \citep{Olson2013, Eisenberg1969}, the majority of tenrecs are very morphologically similar \citep{Jenkins2003} so morphological diversity in the Family as a whole is not as large as it first appears.
+	While there are clear physical differences among family members \citep{Olson2013, Eisenberg1969}, the majority of tenrecs are very morphologically similar \citep{Jenkins2003} so morphological diversity in the family as a whole is not as large as it first appears.
 
@@
 However, it is difficult to quantify overall morphological diversity because any study is inevitably constrained by its choice of specific traits \citep{Roy1997}.
-Variation in skull shape is only one aspect of overall morphology.
-Quantifying variation in other morphological traits could yield different patterns.
+While the skull is widely regarded as a good model for studying morphological variation \citep[e.g.][]{Blagojevic2011, Flores2010, Giannini2010}, quantifying variation in other morphological traits could yield different patterns.
 Therefore future work should extend our approach beyond skulls to gain a more complete understanding of the overall morphological diversity of tenrecs and golden moles.
@@
 	We have presented the first quantitative investigation of morphological diversity in tenrecs.
-Our results indicate that, overall, tenrec skulls are not more morphologically diverse than golden moles and that similarities among the species rich \textit{Microgale} tenrecs mask signals of higher morphological diversity among the rest of the Family.
+Our results indicate that, overall, tenrec skulls are not more morphologically diverse than golden moles and that similarities among the species rich \textit{Microgale} tenrecs mask signals of higher morphological diversity among the rest of the family.
 Of course the results presented here are restricted to just one axis of morphological variation and further analysis of other traits is required.
@@
 Note that the analyses were repeated separately for each set of photographs: skulls in dorsal, ventral and lateral views.
-The dashed arrows refer to the stage at which we selected a subsample of the tenrecs (including just five species of the \textit{Microgale} Genus) so that we could compare the morphological diversity of this reduced subsample of tenrec species to the diversity of golden moles.
+The dashed arrows refer to the stage at which we selected a subsample of the tenrecs (including just five species of the \textit{Microgale} genus) so that we could compare the morphological diversity of this reduced subsample of tenrec species to the diversity of golden moles.
 
@@
 
-% Figure 3: Calculating diversity as mean Euclidean distance to Family centroid.
-% Estimating morphological diversity as the mean Euclidean distance between each species and the Family centroid.
+% Figure 3: Calculating diversity as mean Euclidean distance to family centroid.
+% Estimating morphological diversity as the mean Euclidean distance between each species and the family centroid.
 Every species had scores on the principal components (PC) axes that accounted for 95\% of the variation in the principal components analysis.
 The number of axes (PCn) varied for each analysis but they were the same within a single analysis.
-PC scores were used to calculate the Euclidean distance from each species to the Family centroid (average PC scores for the entire Family).
-Morphological diversity of the Family is the average value of these Euclidean distances.
+PC scores were used to calculate the Euclidean distance from each species to the family centroid (average PC scores for the entire family).
+Morphological diversity of the family is the average value of these Euclidean distances.
 
@@
 % Morphological diversity in tenrecs compared to golden moles (12 species).
-N is the number of tenrec species: 31 species or 17 species including just five representatives of the \textit{Microgale} Genus.
-Morphological diversity of the Family is the mean Euclidean distance from each species to the Family centroid.
+N is the number of tenrec species: 31 species or 17 species including just five representatives of the \textit{Microgale} genus.
+Morphological diversity of the family is the mean Euclidean distance from each species to the family centroid.
 Significant differences between the two Families (p$<$0.05) from two-tailed t-tests are highlighted in bold.
@@
 % Results of the permutation analyses comparing the observed differences in morphological diversity to a null distribution of expected results.
-Morphological diversity of the Family is the mean Euclidean distance from each species to the Family centroid.
+Morphological diversity of the family is the mean Euclidean distance from each species to the family centroid.
 Results are shown for both the full (N=31 species of tenrec compared to 12 species of golden mole) and reduced (N=17 species of tenrec compared to 12 golden moles) data sets.

### 2015-03-12 paper/Manuscript.tex
Changes following reviewers' comments

@@
 Many studies are constrained to measuring the diversity of specific traits rather than overall morphologies \citep{Roy1997}.
-In addition, our perception of morphological diversity is influenced by the trait being used, and results may depend on the particular trait being analysed \citep{Foth2012}.
-Furthermore, linear measurements of morphological traits can restrict our understanding of overall morphological variation; a distance matrix of measurements among specific points is unlikely to give a completely accurate representation of a three dimensional structure \citep{Rohlf1993}.
-Geometric morphometric approaches can circumvent some of these issues by using a system of Cartesian landmark coordinates to define anatomical points \citep{Adams2004}.
+In addition, our perception of morphological diversity is influenced by the trait being measured, and results may depend on the particular trait being analysed \citep{Foth2012}.
+Furthermore, linear measurements of morphological traits can restrict our understanding of overall morphological variation; a distance matrix of measurements among specific points is unlikely to give a complete representation of a three dimensional structure \citep{Rohlf1993}.
+Geometric morphometric approaches can circumvent some of these issues by using a system of Cartesian landmark coordinates to define anatomical points \citep[][and references therein]{Adams2004}.
 This method captures more of the true, overall anatomical shape of particular structures \citep{Mitteroecker2009}.
 In particular, two-dimensional geometric morphometric approaches are commonly used to analyse 3D morphological shape and are appropriate for cross-species comparisons \citep[e.g.][]{Muschick2012, Panchetti2008, Wroe2007}.
-Any bias from 2D representation of a 3D structure is unlikely to be a significant issue for interspecific studies as the overall shape variation among species is geater than discrepancies introduced by using 2D morphometric techniques \citep{Cardinin2014}.
+Any bias from 2D representation of a 3D structure is unlikely to be a significant issue for interspecific studies as the overall shape variation among species is geater than discrepancies introduced by using 2D morphometric techniques \citep{Cardini2014}.
 These more detailed approaches are useful tools for studying patterns of morphological diversity.
@@
 Body masses of tenrecs span three orders of magnitude (2.5 to $>$ 2,000g); a greater range than all other Families, and most Orders, of living mammals \citep{Olson2003}.
-Within this vast size range there are tenrecs which convergently resemble shrews (\textit{Microgale} tenrecs), moles (\textit{Oryzorictes} tenrecs) and hedgehogs \citep[\textit{Echinops} and \textit{Setifer} tenrecs,][]{Eisenberg1969}.
-Their similarities include examples of morphological, behavioural and ecological convergence \citep{Soarimalala2011}.
+Within this vast size range there are tenrecs which resemble shrews (\textit{Microgale} tenrecs), moles (\textit{Oryzorictes} tenrecs) and hedgehogs \citep[\textit{Echinops} and \textit{Setifer} tenrecs,][]{Eisenberg1969}.
+The similarities among tenrecs and other small mammal species include examples of morphological, behavioural and ecological convergence \citep{Soarimalala2011}.
 Tenrecs are one of only four endemic mammalian clades in Madagascar and the small mammal species they resemble are absent from the island \citep{Garbutt1999}.
@@
 
-	Although tenrecs are often cited as an example of both an adaptive radiation and exceptional convergent evolution \citep{Soarimalala2011, Eisenberg1969}, these claims have not been investigated quantitatively.
+	The claims that tenrecs are an example of both an adaptive radiation and convergent evolution have not been investigated quantitatively.
 There are qualitative similarities among the hind limb morphologies of tenrecs and several other unrelated species with similar locomotory styles \citep{Salton2009} but the degree of morphological similarity has not been established.
@@
 In contrast, all golden moles occupy very similar, fossorial ecological niches \citep{Bronner1995}.
-Greater ecological variety is often (though not always) correlated with higher morphological diversity \citep{Losos2010a}.
+Greater ecological variety is often \citep[though not always:][]{McGee2013, Losos2010a} correlated with higher morphological diversity.
 However, our results reveal that, in skulls at least, morphological diversity in tenrecs is not as great as it first appears.
@@
 We used the taxonomy in Wilson \& Reeder's Mammal Species of the World \citeyearpar{Wilson2005}, except for the recently discovered tenrec species \textit{Microgale jobihely} \citep{Goodman2006}.
-We photographed all of the tenrec and golden mole skulls available in the collections.
+We photographed all of the intact tenrec and golden mole skulls available in the collections.
 This included 31 of the 34 species in the tenrec family \citep{Olson2013} and 12 of the 21 species of golden moles \citep{Wilson2005}.
@@
 We photographed the specimens with a Canon EOS 650D camera fitted with a EF 100 mm f/2.8 Macro USM lens and using a remote control (H\"ahnel Combi TF) to avoid camera shake.
-We photographed the specimens on a black material background with a light source in the top left-hand corner of the photograph.
+We photographed the specimens on a black material background with a light source in the top left-hand corner of the photograph and a scale bar placed below the specimen.
 We used small bean bags to hold the specimens in position to ensure that they lay in a flat plane relative to the camera, and used the grid-line function on the live-view display screen of the camera to position the specimens in the centre of each image.
@@
 Our final data sets included photographs of 182 skulls in dorsal view (148 tenrecs and 34 golden moles), 173 skulls in ventral view (141 tenrecs and 32 golden moles) and 171 skulls in lateral view (140 tenrecs and 31 golden moles).
-After taking the photographs we converted the raw files to binary (grey scale) images and re-saved them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}.
+After taking the photographs we used the Canon Digital Photo Professional software \citep{DPP2013} to convert the raw files to binary (grey scale) images and re-save them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}.
 Photographs of the specimens from the American Museum of Natural History and the Smithsonian Institute Natural History Museum are available on figshare (dorsal; \citet{Finlay2013d}, ventral; \citet{Finlay2013v} and lateral; \citet{Finlay2013l}).
-Copyright restrictions from the other museums prevent public sharing of their images but they are available on request.
+Copyright restrictions from the other museums prevent public sharing of their images but they are available from the authors on request.
 
@@
 that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012} to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.
+We used 54 points for skulls in dorsal view (10 landmarks, 44 semilandmarks across 4 curves), 73 points for skulls in ventral view (13 landmarks, 60 semilandmarks) and 44 points for skulls in lateral view (9 landmarks and 35 semilandmarks across 2 curves) (see Figure 2 and the supplementary material for more details).
 
@@
 Second, we compared morphological diversity within tenrecs to the diversity within golden moles.
+
+	Morphological diversity (variation in form) is more commonly referred to as morphological disparity \citep{Foote1997}.
+There are many different methods for measuring disparity.
+Calculations based on summary (principal component) axes of shape variation are popular \citep[e.g.][]{Ruta2013, Foth2012, Brusatte2008, Wainwright2007} while other methods include calculating disparity directly from Procrustes shape variables \citep{Zelditch2012} or rate-based approaches which depend on phylogenetic branching patterns \citep[e.g.][]{Price2013, Price2010, OMeara2006}.
+There is no single best method of measuring disparity \citep{Ciampaglio2001} and each method makes different assumptions which are appropriate for different situations.
+Therefore, for clarity, we have chosen to measure variation in physical form using a clear, easily-interpretable method which captures variation in morphological diversity.
+
 	We define morphological diversity as the mean Euclidean distance (sum of squared differences) between each species and its family centroid (Figure 3).
@@
 This appears to be the case for our data; it was only when we included a sub-sample of \textit{Microgale} tenrecs that we found higher morphological diversity in tenrecs compared to golden moles across all three skull analyses (Table 1).
-	While there are clear physical differences among family members \citep{Olson2013, Eisenberg1969}, the majority of tenrecs are very morphologically similar \citep{Jenkins2003} so morphological diversity in the family as a whole is not as large as it first appears.
+	While there are clear physical differences among family members \citep{Olson2013, Eisenberg1969}, the majority of tenrecs (the \textit{Microgale}) are very morphologically similar \citep{Jenkins2003} so morphological diversity in the family as a whole is not as large as it first appears.
 
-	The goal of our study was to quantify morphological variation in tenrecs instead of relying on subjective assessments of their high morphological diversity \citep{Olson2013, Soarimalala2011, Eisenberg1969}.
+	The goal of our study was to quantify morphological variation in tenrecs instead of relying on subjective assessments of their high morphological diversity.
 However, it is difficult to quantify overall morphological diversity because any study is inevitably constrained by its choice of specific traits \citep{Roy1997}.
@@
 Our results indicate that, overall, tenrec skulls are not more morphologically diverse than golden moles and that similarities among the species rich \textit{Microgale} tenrecs mask signals of higher morphological diversity among the rest of the family.
-Of course the results presented here are restricted to just one axis of morphological variation and further analysis of other traits is required.
+Of course the results presented here are restricted to just one aspect of morphological variation and further analysis of other traits is required.
 However, our findings provide a foundation for future investigations and represent a significant step towards a more quantitative understanding of patterns of morphological and evolutionary diversity in tenrecs.
@@
 % Estimating morphological diversity as the mean Euclidean distance between each species and the family centroid.
-Every species had scores on the principal components (PC) axes that accounted for 95\% of the variation in the principal components analysis.
+Every species had scores on the principal components (PC) axes that accounted for 95% of the variation in the principal components analysis.
 The number of axes (PCn) varied for each analysis but they were the same within a single analysis.

### 2015-03-18 paper/Diversity_supplementary.tex
Separate submission folder, table labelling in supplementary
formatting changes
Reviewer comments on figures, added supplementary sample size table

@@
 Therefore, we are confident that shape variation among the specimens in the rest of the analyses reflects true morphological differences rather than methodological error.
+%---------------------------------------
+\section{Sample size}
 
+The total number of photographs used for each analysis differed slightly because some skull specimens were damaged and could only be used for certain views (see main text).
+Table \ref{tab:samp} summarises the total number of specimens used for each of the three analyses.
+We accounted for differences in sample size by analysing the average skull shape of each species and using permutation tests to ensure that differences in relative morphological diversity were not artefacts of differences in overall group size (see main text).
+
+\begin{table}[!htbp] 
+\caption[Sample size]
+		{Summary of the sample size (number of skull specimens) used for each analysis: skulls in dorsal, ventral and lateral view.} 
+\input{tables/sample.size}
+\label{tab:samp}
+\end{table}
+\newpage
 \bibliographystyle{sysbio} 

### 2015-03-19 paper/Manuscript.tex
Reviewer comments on figures, added supplementary sample size table
Changes for reviewer comments

@@
 Our final data sets included photographs of 182 skulls in dorsal view (148 tenrecs and 34 golden moles), 173 skulls in ventral view (141 tenrecs and 32 golden moles) and 171 skulls in lateral view (140 tenrecs and 31 golden moles).
+Details of the total sample size for each species can be found in the supplementary material.
+
 	After taking the photographs we used the Canon Digital Photo Professional software \citep{DPP2013} to convert the raw files to binary (grey scale) images and re-save them as TIFF files \citep[uncompressed files preserve greater detail, ][]{RHOI2013}.
@@
 For landmarks defined by dental structures, we used published dental sources where available \citep{Repenning1967, Eisenberg1969, Nowak1983, MacPhee1987, KnoxJones1992, Davis1997, Querouil2001, Nagorsen2002, Wilson2005, Goodman2006, Karatas2007, Hoffmann2008, Asher2008,  Muldoon2009, Lin2010}  to identify the number and type of teeth in each species.
-Detailed descriptions of the landmarks can be found in the supplementary material.
+Detailed descriptions of the landmarks, as well as an example figure of landmarks on golden mole skulls, can be found in the supplementary material.
 
@@
 In contrast, our landmarks in the dorsal, and particularly ventral, views focus on morphological variation in the overall outline shape of the sides of the skull and palate (Figure 2).
-The result that tenrecs are no more diverse than golden moles in these areas makes intuitive sense: most tenrecs have broad, non-specialised diets \citep{Olson2013} so there is no obvious functional reason why they should have particularly diverse palate morphologies.
+The result that tenrecs are no more diverse than golden moles in these areas makes intuitive sense: most tenrecs have non-specialised insectivorous or faunivorous diets \citep{Olson2013} so there is no obvious functional reason why they should have particularly diverse palate morphologies.
+Similarly, while there are anatomical differences among tenrec tooth morphologies \citep{Asher2005} more work is required to determine if and how those differences correspond to variation in diet or feeding ecology.
 The different results for our analysis of lateral skull morphologies compared to dorsal and ventral views highlight the importance of using multiple approaches when studying 3D morphological shape using 2D geometric morphometrics techniques \citep{Arnqvist1998}.
@@
 See the supplementary material for detailed landmark descriptions.
-The skulls are two different specimens of \textit{Potamogale velox} (otter shrew tenrec), museum accession numbers AMNH 51327 (dorsal picture) and BMNH 1934.6.16.2 (ventral and lateral pictures).
+The skulls are an example of a \textit{Potamogale velox} (otter shrew tenrec), museum accession number BMNH 1934.6.16.2.
 

### 2015-03-23 analyses/diversity_semilandmarks_resampling.r
Semilandmark resampling in response to reviewer's comments

@@ -1,0 +1,238 @@
+#23/03/15
+
+#Sensitivity analysis in response to reviewer's comments
+
+#Concern that the number of semilandmarks is over-sampling and introduces error in measurement of shape variation
+
+#steps:
+  #1) Read in a clean up raw landmark data  (select just tenrecs and golden moles)
+  
+  #2) Procrustes superimposition of tenrecs and golden moles
+  
+  #3) Randomly resample the number of semilandmarks
+    
+  #4) Find the average Procrustes shape coordinates for each species
+  #5) PCA of the shape coordinates
+  #6) Select PC axes that account for 95% of the variation
+
+  #Repeat steps 3-6 for 25%, 50% and 75% of the total number of semilandmarks, 100 samples of each %
+
+  #Output: table of the number of PC axes that account for 95% of the variation after every analysis
+  
+library(geomorph)
+library(vegan)
+library(plotrix)
+
+source("C:/Users/sfinlay/Desktop/Diversity/functions/Morpho_diversity_functions.r")
+
+setwd("C:/Users/sfinlay/Desktop/Diversity/data/")
+
+#######################
+#Read in the data: 3 views of skulls
+#################
+#SkDors
+    #1) Landmarks
+      land <- readland.tps(file="skdors/Skdors_16_12_13_10landmarks+4curves_edited.TPS")
+    #2) Sliders
+      curves <- as.matrix(read.table("skdors/Skdors_16_12_13_10landmarks+4curves_sliders_edited.NTS", header=TRUE))
+    #3) Taxonomy
+      taxa <- read.csv ("skdors/Skdors_16_12_13_10landmarks_images+specimens.csv" , header=T)
+    #4) Specimens to remove
+      #Null
+
+#-----------------------------------------------------
+#SkVent
+  #1) Landmarks
+    #land <- readland.tps(file="skvent/SkVent_30_10_13_13landmarks+1curve_edited.TPS")
+  #2) Sliders
+    #curves <- as.matrix(read.table(file="skvent/SkVent_1skull_13landmarks+1curve_sliders_edited.tps", header=TRUE))     #this is a tps file and the others are nts but it doesn't make a difference
+  #3) Taxonomy
+    #taxa <- read.csv("skvent/SkVent_30_10_13_imagelist+specimens.csv" , header=TRUE)
+  #4) Specimens to remove
+    #rem <- read.csv("skvent/SkVent_remove_spec.csv", header=T)
+
[…]

### 2015-03-23 functions/Morpho_diversity_functions.r

@@ -19,6 +19,9 @@
     # group.diff
     # pvalue.dist
     
+#4) Sensitivity analysis (response to reviewer's comments)
+    
+    
 ####################################
 #1) General functions
 ######################
@@ -227,3 +230,39 @@ pvalue.dist <- function(distribution,obs.val){
     #but return the actual p value
   return(p)
 }
+#######################################################
+#4) Sensitivity analysis
+
+  #Function to select a random subsample of semilandmarks
+    #Select a random sample of rows in a matrix
+    semilandmark.subsample <- function(landmarks, semilandmarks, percentage){
+      semilandmark.rows <- c((1+landmarks):(semilandmarks+landmarks))
+        samp.semi <- sort(sample(semilandmark.rows, size=(semilandmarks*percentage), replace=F))
+        return(samp.semi)
+      }
+      
+#Wrapper function to have multiple steps together: 
+  #find the number of PC axes that account for 95% of the variation with a specific subsample of semilandmarks
+
+   semilandmark.subsample.PC95axes <- function (landmarks, semilandmarks, percentage){
+   
+  #1) Select a random sample of rows in a matrix (random selection of the semi landmark rows 
+      semilandmark.rows <- c((1+landmarks):(semilandmarks+landmarks))
+      samp.semi <- sort(sample(semilandmark.rows, size=(semilandmarks*percentage), replace=F))       
+        
+  #2) Combine landmark data with subsample of semilandmark data (~NB centroids issue)
+      Proc.co.sub <- list(coords.samp=Proc.co$coords[c(1:landmarks,samp.semi),,], csize=mydataGPA$Csize,ID=mydata$ID,SpecID=mydata$SpecID,
+                  Order=mydata$Order, Fam=mydata$Fam, Genus=mydata$Genus, Species=mydata$Species, Binom=mydata$Binom)
+  #3) Species averaging
+      # group the arrays of coordinates according to species
+        group.sps.coords <- species.coordinates(Proc.co.sub$coords.samp, Proc.co.sub$Binom)
+      #average coordinate values for each species
+        sps.mean <- mean.coords(group.sps.coords)
+  #4) PCA
+      sps.meanPCA <- plotTangentSpace(sps.mean$meanshape, axis1 = 1, axis2 = 2,warpgrids = TRUE, label = TRUE)
+
+  #5) Select the number of PC axes
+      PC95 <- dim(selectPCaxes(sps.meanPCA, 0.956, sps.mean$Binom))[2]
+      
+      return(PC95)
+      }

### 2015-03-24 paper/Diversity_supplementary.tex
Added golden mole diagram to the supplementary, semilandmark subsampling for each skull view

@@
 	The information below provides further details about the landmarks we used to summarise morphological shape in tenrec and golden mole skulls.
-Landmark numbers and curve descriptions refer to Figure 2 in the main paper.
+Landmark numbers and curve descriptions refer to Figure 2 in the main paper (example of a tenrec skull) and also Figure S1 (example golden mole skull).
 One of us (SF) placed all of the landmarks on each picture.
+
+	\begin{figure}[!htbp]
+	\centering
+	\includegraphics[width=0.8\linewidth, height=0.8\textheight, keepaspectratio]{figures/Gmole_combined_col_light.png}
+	\caption[]
+		{Landmarks (numbered points) and curves (outlines) for the skulls in dorsal,ventral and lateral view.
+See Tables S1, S2 and S3 for more detailed landmark descriptions.
+The skulls are an example of a \textit{Chlorotalpa duthieae} (Duthie's golden mole), museum accession number AMNH 161527.}
+	\label{fig:gmole}
+	\end{figure}
 

### 2015-03-24 analyses/diversity_semilandmarks_resampling.r

@@ -32,11 +32,11 @@ setwd("C:/Users/sfinlay/Desktop/Diversity/data/")
 #################
 #SkDors
     #1) Landmarks
-      land <- readland.tps(file="skdors/Skdors_16_12_13_10landmarks+4curves_edited.TPS")
+      #land <- readland.tps(file="skdors/Skdors_16_12_13_10landmarks+4curves_edited.TPS")
     #2) Sliders
-      curves <- as.matrix(read.table("skdors/Skdors_16_12_13_10landmarks+4curves_sliders_edited.NTS", header=TRUE))
+      #curves <- as.matrix(read.table("skdors/Skdors_16_12_13_10landmarks+4curves_sliders_edited.NTS", header=TRUE))
     #3) Taxonomy
-      taxa <- read.csv ("skdors/Skdors_16_12_13_10landmarks_images+specimens.csv" , header=T)
+      #taxa <- read.csv ("skdors/Skdors_16_12_13_10landmarks_images+specimens.csv" , header=T)
     #4) Specimens to remove
       #Null
 
@@ -54,13 +54,13 @@ setwd("C:/Users/sfinlay/Desktop/Diversity/data/")
 #--------------------------------------------------------
 #SkLat
   #1) Landmarks
-    #land <- readland.tps(file="sklat/SkLat_08_11_13_9landmarks_2curves_edited.TPS")
+    land <- readland.tps(file="sklat/SkLat_08_11_13_9landmarks_2curves_edited.TPS")
   #2) Sliders
-    #curves <- as.matrix(read.table(file="sklat/SkLat_08_11_13_9landmarks_2curves_sliders_edited.NTS", header=TRUE))
+    curves <- as.matrix(read.table(file="sklat/SkLat_08_11_13_9landmarks_2curves_sliders_edited.NTS", header=TRUE))
   #3) Taxonomy
-    #taxa <- read.csv("sklat/SkLat_08_11_13_Specimens+images.csv", header=TRUE)
+    taxa <- read.csv("sklat/SkLat_08_11_13_Specimens+images.csv", header=TRUE)
   #4) Specimens to remove
-    #rem <- read.csv("sklat/SkLat_remove_spec.csv", header=T)
+    rem <- read.csv("sklat/SkLat_remove_spec.csv", header=T)
 
 
 #################################################
@@ -155,9 +155,9 @@ setwd("C:/Users/sfinlay/Desktop/Diversity/data/")
   #sk.landmarks <- 13
   #sk.semilandmarks <- 60
   
[…]

### 2015-03-24 paper/PeerJ_resubmission/Manuscript.tex
Full responses to reviewers, documents ready in the resubmission folder

--- 2015-03-19 paper/Manuscript.tex
@@
 
-	% Morphological diversity is often studied qualitatively.
-However, to truly understand the evolution of exceptional diversity, it is important to take a quantitative approach instead of relying on subjective, qualitative assessments.
+	%It is important to quantify patterns of morphological diversity to enhance our understanding of variation in ecological and evolutionary traits.
 Here, we present a quantitative analysis of morphological diversity in a family of small mammals, the tenrecs (Afrosoricida, Tenrecidae).
@@
 
-	% Contrary to our expectations, We find that tenrec skulls are only more morphologically diverse than golden moles when measured in lateral view.
+	% Contrary to our expectations, we find that tenrec skulls are only more morphologically diverse than golden moles when measured in lateral view.
 Furthermore, similarities among the species-rich \textit{Microgale} tenrec genus appear to mask higher morphological diversity in the rest of the family.
@@
 The family is comprised of 34 species, 31 of which are endemic to Madagascar \citep{Olson2013}.
-Body masses of tenrecs span three orders of magnitude (2.5 to $>$ 2,000g); a greater range than all other Families, and most Orders, of living mammals \citep{Olson2003}.
+Body masses of tenrecs span three orders of magnitude (2.5 to $>$ 2,000g): a greater range than all other families, and most orders, of living mammals \citep{Olson2003}.
 Within this vast size range there are tenrecs which resemble shrews (\textit{Microgale} tenrecs), moles (\textit{Oryzorictes} tenrecs) and hedgehogs \citep[\textit{Echinops} and \textit{Setifer} tenrecs,][]{Eisenberg1969}.
@@
 Tenrecs are one of only four endemic mammalian clades in Madagascar and the small mammal species they resemble are absent from the island \citep{Garbutt1999}.
-Therefore, it appears that tenrecs represent an adaptive radiation of species which filled otherwise vacant ecological niches \citep{Soarimalala2011}.
+Therefore, it appears that tenrecs represent an adaptive radiation of species which filled otherwise vacant ecological niches through gradual morphological specialisations \citep{Poux2008}.
 
@@
 that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012} to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.
-We used 54 points for skulls in dorsal view (10 landmarks, 44 semilandmarks across 4 curves), 73 points for skulls in ventral view (13 landmarks, 60 semilandmarks) and 44 points for skulls in lateral view (9 landmarks and 35 semilandmarks across 2 curves) (see Figure 2 and the supplementary material for more details).
+We used 54 points for skulls in dorsal view (10 landmarks, 44 semilandmarks across 4 curves), 73 points for skulls in ventral view (13 landmarks, 60 semilandmarks) and 44 points for skulls in lateral view (9 landmarks and 35 semilandmarks across 2 curves).
+See Figure 2 and the supplementary material for more details.
 
@@
 First, we used non parametric multivariate analysis of variance \citep[npMANOVA;][]{Anderson2001} to test whether tenrecs and golden moles occupied significantly different positions within the morphospaces defined by the PC axes that accounted for 95\% of the overall variation in the data \citep[e.g.][]{Serb2011, Ruta2013}.
-A significant difference between the two Families would indicate that they have unique morphologies which do not overlap.
+A significant difference between the two families would indicate that they have unique morphologies which do not overlap.
 Second, we compared morphological diversity within tenrecs to the diversity within golden moles.
@@
 
-	One possible issue with these analyses is that the two Families have unequal sample sizes: 31 (or a subset of 17) tenrec species compared to just 12 golden mole species.
+	One possible issue with these analyses is that the two families have unequal sample sizes: 31 (or a subset of 17) tenrec species compared to just 12 golden mole species.
 Morphological diversity is usually decoupled from taxonomic diversity \citep[e.g.][]{Ruta2013, Hopkins2013} so larger groups are not necessarily more morphologically diverse.
@@
 	We performed this shuffling procedure (random assignation of group identity) 1000 times and calculated the difference in morphological diversity between the two groups for each permutation.
-This generated a distribution of 1000 values which are calculations of the differences in morphological diversity under the assumption that the null hypothesis (equal morphological diversity in the two Families) is true.
+This generated a distribution of 1000 values which are calculations of the differences in morphological diversity under the assumption that the null hypothesis (equal morphological diversity in the two families) is true.
 This method automatically accounts for differences in sample size because shuffling of the group labels preserves the sample size of each group: there will always be 12 species labelled as "golden mole" and then, depending on the analysis, either 31 or 17 species labelled as "tenrec".
 Therefore, the 1000 permuted values of differences in morphological diversity create a distribution of the expected difference in diversity between a group of sample size 31 (or 17 in the case of the tenrec data subset) compared to a group of sample size 12 under the null hypothesis that the two groups have the same morphological diversity.
-We compared the observed measures of the differences in morphological diversity between the two Families to these null distributions to determine whether there were significant differences after taking sample size into account (two-tailed t test).
+We compared the observed measures of the differences in morphological diversity between the two families to these null distributions to determine whether there were significant differences after taking sample size into account (two-tailed t test).
 Data and code for all of our analyses are available on GitHub \citep{Finlay2015c}.
@@
 
-	To compare morphological diversity in the two Families, we used the PC axes which accounted for 95\% of the cumulative variation in each of the skull analyses: dorsal (n=6 axes), ventral (n=7 axes) and lateral (n=7 axes).
+	To compare morphological diversity in the two families, we used the PC axes which accounted for 95\% of the cumulative variation in each of the skull analyses: dorsal (n=6 axes), ventral (n=7 axes) and lateral (n=7 axes).
 First, we compared the position of each family within the morphospace plots.
-Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72, p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001) skull morphospaces, indicating that the Families have very different, non-overlapping cranial and mandible morphologies (Figure 4).
+Tenrecs and golden moles occupy significantly different positions in the dorsal (npMANOVA: F\textsubscript{1,42}=68.13, R$^2$=0.62, p=0.001), ventral (npMANOVA: F\textsubscript{1,42}=103.33, R$^2$=0.72, p=0.001 ) and lateral (npMANOVA: F\textsubscript{1,42}=76.7, R$^2$ =0.65, p=0.001) skull morphospaces, indicating that the families have very different, non-overlapping cranial and mandible morphologies (Figure 4).
+For each analysis, PC1 summarises a morphological change from the foreshortened, "squat" shape of golden mole skulls at one extreme to the rostrally elongated shape of tenrecs (particularly the \textit{Microgale}) at the other extreme.
+
 	Second, we compared the morphological diversity within each family.
@@
 	We thank Thomas Guillerme, Fran\c{c}ois Gould and the members of NERD club for their insightful discussions and comments.
+We are grateful to the Editor, Nick Crumpton and an anonymous reviewer for their constructive comments.
 Thank you to museum staff and curators for facilitating our access to their collections: Leona Leonard and Nigel Monaghan (Natural History Museum, Ireland), Roberto Portela Miguez and Paula Jenkins (Natural History Museum, London), Esther Langan (Smithsonian Institute NMNH), Eileen Westwig (American Museum of Natural History), Judy Chupasko (Museum of Comparative Zoology) and Bill Stanley and Steve Goodman (Field Museum).

### 2015-03-24 analyses/diversity_PCAplots_3panel.r

@@ -212,6 +212,10 @@ par(mar=c(5,5,4,4), mfrow=c(2,2))
       axis(side=2, at=0, las=1, cex.axis=1.3)
     #add dotted lines along 0,0
       abline(0,0, h=0, v=0, lty=2, lwd=1)
+ 
+ #identify points
+#identify(skdors.xaxis, skdors.yaxis,labels=(skdors.sp.fam$Binom))
+ 
       
 #SkVent
   plot(skvent.xaxis, skvent.yaxis, xlab="", ylab="", las=1,
@@ -225,6 +229,8 @@ par(mar=c(5,5,4,4), mfrow=c(2,2))
     #add dotted lines along 0,0
       abline(0,0, h=0, v=0, lty=2, lwd=1)
 
+ #identify points
+#identify(skvent.xaxis, skvent.yaxis,labels=(skvent.sp.fam$Binom))
 
 #SkLat
   plot(sklat.xaxis, sklat.yaxis, xlab="", ylab="", las=1,
@@ -237,12 +243,12 @@ par(mar=c(5,5,4,4), mfrow=c(2,2))
       axis(side=2, at=0, las=1, cex.axis=1.3)
     #add dotted lines along 0,0
       abline(0,0, h=0, v=0, lty=2, lwd=1)
-      
+ #identify points
+#identify(sklat.xaxis, sklat.yaxis,labels=(sklat.sp.fam$Binom))      
 
 
 
-#identify points
-#identify(mands.xaxis, mands.yaxis,labels=(mands.sp.fam$Binom))
+
 
 #I copied and pasted the plots into a powerpoint presentation and added the labels to the axes
   #Saved within Diversity/output/shapedata

### 2015-03-24 analyses/diversity_semilandmarks_resampling.r

@@ -97,29 +97,8 @@ setwd("C:/Users/sfinlay/Desktop/Diversity/data/")
   mydata <- select.from.list(combine, tc.gm)
   mydata <- droplevels.from.list(mydata)
   
-###################################
-#Resample the number of semilandmarks
-########################
-
-#Identify the rows which are semilandmarks (not landmarks)
-  #The number will be different for each analysis
-  
-  #Skulls Dorsal: 10 landmarks and 44 semilandmarks
-    #semilandmarks <- c(11:dim(mydata$land)[1])
-    
-  #Select a random sample of the semilandmarks (retain a percentage of the total number of semilandmarks)
-      #samp.semi50 <- sort(sample(semilandmarks, size=(dim(mydata$land)[1])/2, replace=F))
-      
-  #Select the landmarks along with the subsample of semilandmarks
-      #mydata$land[c(1:10,samp.semi50),,]
-      
-#Problem with curves: identify sliders based on the original landmarks and semilandmarks
-  # random re-sampling of the curves rows wouldn't make sense
-#BACK TO HERE
-
-
 ##############################################
-#Procrustes superimposition before resampling semilandmarks
+#Procrustes superimposition 
 ##########################################
 #General Procrustes Alignment of all of the scaled coordinates
   mydataGPA <- gpagen(mydata$land, curves=mydata$curves, ProcD=TRUE,)
@@ -235,4 +214,4 @@ setwd("C:/Users/sfinlay/Desktop/Diversity/output/semilandmark_resampling")
     #capture.output(PC.table, file= "skvent_PCresamp.tab.txt")
 
 #Sklat
-    capture.output(PC.table, file= "sklat_PCresamp.tab.txt")
+    #capture.output(PC.table, file= "sklat_PCresamp.tab.txt")

### 2015-03-24 functions/Morpho_diversity_functions.r

@@ -20,7 +20,8 @@
     # pvalue.dist
     
 #4) Sensitivity analysis (response to reviewer's comments)
-    
+    #semilandmark.subsample
+    #semilandmark.subsample.PC95axes
     
 ####################################
 #1) General functions

### 2015-03-28 paper/PeerJ_resubmission/Supplemental_S1.tex
Figure and supplemental edits after PeerJ request

--- 2015-03-24 paper/Diversity_supplementary.tex
@@
 	\centering
-	\includegraphics[width=0.8\linewidth, height=0.8\textheight, keepaspectratio]{figures/Gmole_combined_col_light.png}
+	\includegraphics[width=0.8\linewidth, height=0.8\textheight, keepaspectratio]{figures/Gmole_combined_col_light_labels.png}
 	\caption[]
-		{Landmarks (numbered points) and curves (outlines) for the skulls in dorsal,ventral and lateral view.
+		{Landmarks (numbered points) and curves (outlines) for the skulls in dorsal (A), ventral (B) and lateral (C) view.
 See Tables S1, S2 and S3 for more detailed landmark descriptions.

### 2015-04-13 paper/PeerJ_resubmission/Manuscript.tex
Figure and supplemental edits after PeerJ request
Update after PeerJ acceptance: edits to manuscript and new version of figure 2

@@
 We used the taxonomy in Wilson \& Reeder's Mammal Species of the World \citeyearpar{Wilson2005}, except for the recently discovered tenrec species \textit{Microgale jobihely} \citep{Goodman2006}.
-We photographed all of the intact tenrec and golden mole skulls available in the collections.
+We photographed all of the undamaged tenrec and golden mole skulls available in the collections.
 This included 31 of the 34 species in the tenrec family \citep{Olson2013} and 12 of the 21 species of golden moles \citep{Wilson2005}.
@@
 For landmarks defined by dental structures, we used published dental sources where available \citep{Repenning1967, Eisenberg1969, Nowak1983, MacPhee1987, KnoxJones1992, Davis1997, Querouil2001, Nagorsen2002, Wilson2005, Goodman2006, Karatas2007, Hoffmann2008, Asher2008,  Muldoon2009, Lin2010}  to identify the number and type of teeth in each species.
-Detailed descriptions of the landmarks, as well as an example figure of landmarks on golden mole skulls, can be found in the supplementary material.
+Detailed descriptions of the landmarks can be found in the supplementary material (Tables S1, S2, S3) along with an example figure of landmarks on golden mole skulls (figure S1).
 
@@
 To ensure that we applied a uniform standard of shape representation to each outline segment (i.e.
-that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012} to determine the minimum number of semilandmark points which would give accurate representations of morphological shape.
-We used 54 points for skulls in dorsal view (10 landmarks, 44 semilandmarks across 4 curves), 73 points for skulls in ventral view (13 landmarks, 60 semilandmarks) and 44 points for skulls in lateral view (9 landmarks and 35 semilandmarks across 2 curves).
+that simple structures would not be over-represented and more complex features would not be under-represented), we followed the method outlined by MacLeod \citeyearpar{MacLeod2012}.
+This re-sampling method determines the minimum number of semilandmark points required to measure an outline length to at least 95\% accuracy of the true length of the outline.
+The procedure balances the need to represent outline shapes accurately without introducing error by over-sampling curves \citep{MacLeod2012}.
+We used 54 points for skulls in dorsal view (10 landmarks, 44 semilandmarks across 4 curves, Table S1), 73 points for skulls in ventral view (13 landmarks, 60 semilandmarks, Table S2) and 44 points for skulls in lateral view (9 landmarks and 35 semilandmarks across 2 curves, Table S3).
 See Figure 2 and the supplementary material for more details.
@@
 	We tested the null hypothesis that tenrecs and golden moles have the same morphological diversity (the same mean Euclidean distance to the family centroid).
-If this is true, when we randomly assign the group identity of each species (i.e.
+If this is supported, when we randomly assign the group identity of each species (i.e.
 shuffle the "tenrec" and "golden mole" labels) and then re-compare the morphological diversity of the two groups, there should be no significant difference between these results and those obtained when the species are assigned to the correct groupings.
@@
 This method automatically accounts for differences in sample size because shuffling of the group labels preserves the sample size of each group: there will always be 12 species labelled as "golden mole" and then, depending on the analysis, either 31 or 17 species labelled as "tenrec".
-Therefore, the 1000 permuted values of differences in morphological diversity create a distribution of the expected difference in diversity between a group of sample size 31 (or 17 in the case of the tenrec data subset) compared to a group of sample size 12 under the null hypothesis that the two groups have the same morphological diversity.
+Therefore, the 1000 permuted values of differences in morphological diversity create a distribution of the expected difference in diversity between a group of sample size N=31 (or N=17 in the case of the tenrec data subset) compared to a group of sample size N=12 under the null hypothesis that the two groups have the same morphological diversity.
 We compared the observed measures of the differences in morphological diversity between the two families to these null distributions to determine whether there were significant differences after taking sample size into account (two-tailed t test).
@@
 % Figure 2: Skulls: dorsal, ventral and lateral landmarks
-% Landmarks (numbered points) and curves (outlines) for the skulls in dorsal,ventral and lateral view.
+% Landmarks (numbered points) and curves (outlines) for the skulls in dorsal (A),ventral (B) and lateral (C) view.
 See the supplementary material for detailed landmark descriptions.
@@
 % Figure 4: Morphospace (principal components) plot of morphological diversity in tenrec and golden mole skulls
-% Principal components plots of the morphospaces occupied by tenrecs (triangles, n=31 species) and golden moles (circles, n=12 species) for skulls in dorsal (top left), ventral (top right) and lateral (bottom left) views.
+% Principal components plots of the morphospaces occupied by tenrecs (triangles, n=31 species) and golden moles (circles, n=12 species) for skulls in dorsal (A), ventral (B) and lateral (C) views.
 Each point represents the average skull shape of an individual species.
